# Methods

## SURVEY DESIGN

Design for the `r yr` and  `r yr + 1` sablefish research and assessment survey employed a stratified random sampling (StRS) component and a traditional component consisting of standardized sets at offshore indexing localities and at mainland inlets.  In `r yr+1`, fishing at offshore indexing sites was discontinued (Table \@ref(tab:Table1)).  

Under the StRs component, random fishing sets were conducted in five spatial strata and three depth strata (Figure \@ref(fig:figure2), and Figure \@ref(fig:figure3)).  The traditional component consisted of standardized fishing sets at nine offshore indexing sites (Figure \@ref(fig:figure2), and Figure \@ref(fig:figure3)) and at four mainland inlets (Figure \@ref(fig:figure4)).  In addition, exploratory sets were conducted in `r yr+1` at North Vancouver Island near Cliffe Point and Koskimo Bay (Figure \@ref(fig:figure3)). 

### STRATIFIED RANDOM SAMPLING SURVEY COMPONENT

The StRS design began in 2003 with the purpose of distributing tag releases at random, collecting biological samples and developing a catch-rate based index of abundance [@Wyeth2003]. It also provided an alternative design to the historic traditional offshore component of the survey (1990 to 2010) which occured at fixed locations. 

Under the StRS design, the offshore survey area is partitioned into five spatial strata (S~1~ to S~5~) and three depth strata (RD~1~ to RD~3~) for a total of 15 strata. The five spatial strata are S~1~ (South West Coast Vancouver Island or SWCVI), S~2~ (North West Coast Vancouver Island or NWCVI), S~3~ (Queen Charlotte Sound or QCS), S~4~ (South West Coast of Haida Gwaii or SWCHG), and S~5~ (North West Coast of Haida Gwaii or NWCHG).  The three targeted depth ranges are 100-250 fathoms (RD~1~), 250-450 fathoms (RD~2~), and 450-750 fathoms(RD~3~). The area within each of the 15 strata are divided into 2 km x  2 km grid cells or ‘fishing blocks’ from which set locations are randomly chosen (Figure \@ref(fig:figure1)).  

From 2003 through 2005, five grid cells were randomly selected in each spatial-depth stratum. From 2006 through 2010, the number was increased to six. An analysis was completed for the 2011 survey to optimize the allocation of blocks to strata, resulting in an increase in sets in most stratum (Table \@ref(tab:Table2)). 

### TRADITIONAL OFFSHORE INDEXING SURVEY COMPONENT (2010)

Under the traditional design, five (5) strings of trap gear were set within nine (9) offshore indexing localities:  Barkley Canyon, Esperanza Inlet, Quatsino Sound, Triangle Island, Cape St. James, Gowgaia Bay, Buck Point, Hippa Island and Langara Island-North Frederick, with one string in each of one of five (5) depth intervals: 150-249, 250-349, 350-450, 450-550, and 550-650 fathoms (Table \@ref(tab:Table1)). 

The original intent of the standardized sets was to collect catch rate data in order to index trends in abundance, tag fish and obtain biological samples. After the 2010 survey, the offshore portion of the traditional standardized survey was terminated (Appendix \@ref(app:first-appendix)). It was shown that the continued use of the standardized survey, in combination with the StRS, resulted in greater frequency for stock assessment errors [@Cox2011].

### TRADITIONAL MAINLAND INLET SURVEY COMPONENT

Under the mainland inlet design, a string of twenty-five (25) traps were set at five specific localities in each of the following four (4) areas: Portland Inlet, Gil Island, Finlayson Channel, and Dean/Burke Channel. Trap gear was deployed near the center of each of the five locality boundaries in order to avoid the steep slopes characteristic of these channels/fjords (Figure \@ref(fig:figure4)).

### EXPLORATORY COMPONENT (2011)

To evaluate areas that have not been surveyed for sablefish density and/or size composition, an exploratory sets were conducted in 2011.

## VESSEL

The `r yr` and `r yr + 1` surveys were chartered aboard the F/V `r boat1` (Figure \@ref(fig:figure5)), skippered by `r captain1` between `r dates1`, `r yr` and `r captain2` between `r dates2`, `r yr + 1` (Appendix \@ref(app:second-appendix)).   Further information about the vessel can be found at [\underline{http://marinetraffic.com}](http://marinetraffic.com). 

```{r fishingGear2010-2011, echo=FALSE}
# location for fishing gear and schedules: 
#    \\DFBCV9TWVASP001\Shares$\Data Rescue\SABLEFISH_SCANS\Ocean Pearl_2010.10.09_to_2010.11.30_Trip 70787\01_Notes\Worksheets
#    \\DFBCV9TWVASP001\Shares$\Data Rescue\SABLEFISH_SCANS\Ocean Pearl_2011.10.09_to_2011.11.21_Trip 72067\01_Notes

```

## FISHING GEAR

The longline trap gear consisted of a groundline resting on the ocean floor with 25 baited traps attached to beckets at 150 foot intervals along its length and 90 pound anchors at each end (Figure \@ref(fig:figure6), a). A flagpole was required for at least one end of the set to improve visibility for retrieval. The traps were standard Ladner traps with a bottom hoop diameter of 54 inches and covered with black nylon #48 thread, with a web of 2.75 inch mesh (Figure \@ref(fig:figure6), b). The tunnels were made of green braided, knotless, rashell 2 inch mesh. The traps had stainless steel escape rings closed off by orange twine sewn repeatedly across the ring opening.

Standard bait bags (6 by 12 inches) made of 1/8 inch web with a nylon drawstring and stainless steel halibut longline snap were included with the traps. 

## FISHING OPERATIONS

During normal survey fishing operations gear was deployed on alternate days. Prior to deployment, the Fishing Master inspected the block to determine fishability and if it was within the targeted depth range.  The goal was to have as much gear as possible within the block boundaries.  If unfishable, the survey protocol directs that an alternate block is to be chosen to the east, west, north, and south, respectively. If none of those blocks meet the fishing criteria, an alternate block of the same area and depth strata was randomly chosen.

Two science staff recorded information associated with the deployment of the gear. One science member was positioned in the wheelhouse and entered details about the set in the bridge log data form (Appendix \@ref(app:third-appendix), Figure C.1). The time at deployment of the first buoy and anchor were logged and later, the time at retrieval of the second buoy and anchor were recorded.  The duration of the set was calculated as the time elapsed between the first anchor being set over the stern and the first anchor hauled aboard.  The geo-referenced positions were obtained from Nobeltec Navigation © software running on the bridge computer, transmitted through NMEA sentences. 

A set log was filled out on the deck by the science recorder who had maximum visibility of the crew setting the traps over the stern rail. The set log included the time and identity of the first and last buoys, anchor time, a tally of beckets and traps, as well as the serial number of each Sea-bird Bird SBE 39 temperature and pressure logger.

Sets at offshore indexing localities (2010) had a targeted soak time of 24 hours.  Traps were baited with 1 pound of bagged squid.  StRS blocks also had a targeted soak time of 24 hours.  Fishing sets were designated useable if hauled between 22 and 26 hours. StRS traps were baited with 10 pounds of loose offshore Pacific Hake (*Merluccius productus*) and 2 pounds of bagged squid.  Fishing sets in mainland inlet localities had a targeted soak time of 18 hours. These sets were designated useable if hauled between 16 and 20 hours, compatible with the historic inlet survey protocols.  Traps were baited with 2 pounds of bagged squid (Table \@ref(tab:Table1)). 

## CATCH PROCESSING

As the groundline was hauled, catch by species from each trap were sorted into baskets and entered in the charter catch log form (Appendix \@ref(app:third-appendix), Figure C.2).  Baskets were then weighed to the nearest 0.2 kg on a motion compensating scale and given a basket use code of D, A, B (2010), T or MT.  Code D designated fish species as discards (alive); code A allocated fish to age samples; code B (2010) allocated sablefish for length, sex, maturtiy samples; code T allocated sablefish to be tagged and released; code L allocated fish for length samples; and code MT indicated an empty trap. 

The Federal Court of Appeal ruling (Larocque v. Canada (Minister of Fisheries and Oceans Canada) (Federal Court of Appeal Canada 2006)) was used to support scientific research of key
commercial fish in place of quota allocation. As a result, sablefish in traps assigned code D were released at sea.

Crew members would inform the recorder about any damage to a trap and report the serial number of the temperature and pressure logger.  The next
day, the entries on charter catch log form were transposed to tabular format on the charter catch log entry form (Appendix \@ref(app:third-appendix), Figure C.3).

### Sablefish Allocation Details

In 2010, 50 to 60 sablefish at offshore indexing sites were allocated throughout the string for a biological sample of length, sex, weight, maturity and otoliths (LSWMO). Up to 80 sablefish were allocated along the string for a biological sample of length, sex and maturity (LSM).  StRS sets used a sampling protocol that assigned a fate to the sablefish catch in each trap, dividing the 25 traps so that 1/3 of the traps were used for tagging, 1/3 were used for biological samples (~50 specimens) and 1/3 were released alive. At mainland inlet sites, sablefish catch from 1/2 of the traps were allocated for biosamples (~50 specimens) and 1/2 of the traps were used for tagging (Table \@ref(tab:Table1)).

## BIOLOGICAL SAMPLING

Biological samples were collected from sablefish and rougheye/blackspotted rockfish on the LSWMO form (Appendix \@ref(app:third-appendix), Figure C.4).  Measurements were recorded for fork length (L), body weight (W), sex (S) and maturity level (M). Sagittal otoliths (O) were collected and stored for potential ageing by the sclerochronology laboratory.  In addition, tissue for DNA was collected from the rougheye/blackspotted rockfish specimens for later species determination (Appendix \@ref(app:third-appendix), Figure C.5).  Since this complex of two distinct species [@Orr2008] have similar appearances with slight variations in colour markings and dorsal fin lengths, the sampler visually identifed each specimen as either a rougheye (RE), a blackspotted (BS) or a hybrid (HB) species.  All rockfish and legal-sized sablefish (fork length greater than 55 cm) that were sacrificed for biological samples were dressed, frozen, and landed as commercial catch.  

In 2010, biological samples at offshore indexing localities were obtained from sablefish on the length, sex and maturity (LSM) sampling form (Appendix \@ref(app:third-appendix), Figure C.6). Biological sampling forms were completed for specimens other than sablefish. Species specific length (L) and sex (S) were collected from other species on the LSS form (Appendix \@ref(app:third-appendix), Figure C.7).  


## SABLEFISH TAGGING

Fish destined to be tagged were transferred from the sorting area to a tagging tank.  Sablefish were tagged with a Mark II Long Tagging gun loaded with Floy FD-94 T-bar anchor tags.  The tag was inserted on the left side of the fish, 1 cm below and 2-3 cm behind the anterior insertion of the first dorsal fin.  Fork length (mm to the nearest ½ cm) measurements were taken on the Scantrol measuring board and recorded on the tagging form.  Before release, any sampling errors, injuries or damage to the fish were documented. Tag checks were performed systematically to ensure tag numbers on the data form matched those on the fish specimen (Appendix \@ref(app:third-appendix), Figure C.8).

## SABLEFISH TAG RECOVERY

Any previously tagged fish brought aboard were treated in one of two ways.  First, sablefish with Canadian tags were re-released with a new tag and the previous tag was removed. In addition, any wounds from the old tag were recorded.  Second, sablefish with a foreign agency tag or sablefish that had sustained numerous injuries were retained for biological sampling.  For these specimens, data were recorded on the tag recovery sheet and any foreign tags were returned to their country of origin (Appendix \@ref(app:third-appendix), Figure C.9).


```{r SensorText, echo=FALSE}
   # -- oceanographic sensor text:  determine the number of sets that deployed SBE and/or HOBO and/or CTD

   sense  <-  paste("select Year, SUM(SBE39) AS SBE39, SUM(HOBO) AS HOBO, ",
                    "SUM(CTD) AS CTD, SUM(CAM) AS CAM ",
                    "from dbo.Report_SBE_HOBO_IND ",
                    "group by Year having (Year =", yr,")", sep="")
   #sensor <-  GetSQLData(sense,"Sablefish")   # query SQL Server
   #write.table(sensor, file = paste(path,"methods1.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",") 
   sensor <-  read.csv(paste(path,'methods1.csv',sep=''),header=T)
   
   sense2 <-  paste("select Year, SUM(SBE39) AS SBE39, SUM(HOBO) AS HOBO, ",
                    "SUM(CTD) AS CTD, SUM(CAM) AS CAM ",
                    "from dbo.Report_SBE_HOBO_IND ",
                    "group by Year having (Year =", yr+1,")", sep="")
   #sensor2 <-  GetSQLData(sense2,"Sablefish")  # query SQL Server
   #write.table(sensor2, file = paste(path,"methods2.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",") 
   sensor2 <-  read.csv(paste(path,'methods2.csv',sep=''),header=T)
 
```

## OCEANOGRAPHIC SENSOR DATA COLLECTION

A Sea-bird Bird SBE 39 temperature and pressure logger was placed in a protective plastic pipe and attached to the inside of the third trap on each string.    The logger data in the form of temperature, depth, date and time was downloaded after hauling using the Sea-Bird Electronics SeaTerm © software. 


## ELECTRONIC MONITORING VIDEO DATA COLLECTION  

During haulback, the electronic monitoring (EM) system cameras were activated by the hydraulic sensor.  Standard analog cameras were positioned at optimal viewing angles to record survey activities (Appendix \@ref(app:fourth-appendix)).  Video of catch processed at the hopper was reviewed following the survey in 2010 and corrections were made during post-electronic data entry.  In 2011, the video was reviewed the day after haulback to increase the quality standards of catch data.


\clearpage
