# Results and Discussion

## FISHING

The `r yr` survey was 52 days long, starting in Victoria, BC on October 9, with crew changes on October 17 at Gold River, November 1 at Rose Harbour and November 19 at Masset.  In total, 153 sets were completed; 88 StRS sets at random sites, 45 standardized sets at offshore indexing localities and 20 standardized sets at mainland inlets (Appendix \@ref(app:fifth-appendix)).

The `r yr + 1` survey was 43 days long, commencing in Victoria, BC on October 9, with crew changes on October 20 at Coal Harbour, October 31 at Rose Harbour and November 12 at Masset.  In total, 132 sets were completed; 20 standardized sets at mainland inlets, 110 StRS sets at random sites and 2 sets at exploratory sites.  (Appendix \@ref(app:sixth-appendix)).


```{r CatchRateText, echo=FALSE}
    strat_mean <- read.csv(paste(path,'LandmarkCPUEVarianceCVs_StRS.csv', sep=''), header=T)
    current_year <- yr+1
    # some basic stats, not used in doc but there just in case
    per_change_current <- round(((strat_mean$yStr[strat_mean$SET_YEAR==current_year]/
                                    strat_mean$yStr[strat_mean$SET_YEAR==current_year-1])-1)*100,digits=0)
  
    per_change_avg <- round(((strat_mean$yStr[strat_mean$SET_YEAR==current_year]/
                                              mean(strat_mean$yStr[(length(strat_mean$yStr)-2):(length(strat_mean$yStr)-1)]))-1) * 100, digits=0)
    
    # -- type data.mn in the Console to view the shallow, middle and deep depth stratums CPUE for 
    # -- descriptive paragraph below
       
    # INLET TEXT          
    cpuedt <- "SELECT  * FROM dbo.GENERIC_GFBIO_TRAPS where year < 2012 and [Spatial.Stratum] not like '%Quatsino Sound%' "
    cpuedat<- GetSQLData(cpuedt,"Sablefish") 
    write.table(cpuedat, file = paste(path,"figure11.csv",sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",") 
    cpuedat   <-  read.csv(paste(path,'figure11.csv',sep=''),header=T)

    # pick out the stand sets
    dat          <- cpuedat[ which(cpuedat$SABLE.SET.TYPE=="INLET STANDARDIZED" ), ]
    dat          <- dat[ which(is.na(dat$SABLE.SET.TYPE)==FALSE), ]
    inlet03      <- dat[dat$year == 2003,]
    inlet03.mn   <- round(mean(inlet03$CPUE.SABLE.COUNT/inlet03$CPUE.TRAPS, na.rm=TRUE),0)
    inlet03kg.mn <- round(mean(inlet03$CPUE.SABLE.WEIGHT/inlet03$CPUE.TRAPS),0)
    
    inlet04      <- dat[dat$year == 2004,]
    inlet04.mn   <- round(mean(inlet04$CPUE.SABLE.COUNT/inlet04$CPUE.TRAPS),0)
    inlet04kg.mn <- round(mean(inlet04$CPUE.SABLE.WEIGHT/inlet04$CPUE.TRAPS),0)
    
    inlet98      <- dat[dat$year == 1998,]
    inlet98.mn   <- round(mean(inlet98$CPUE.SABLE.COUNT/inlet98$CPUE.TRAPS),0)
    inlet98kg.mn <- round(mean(inlet98$CPUE.SABLE.WEIGHT/inlet98$CPUE.TRAPS),0)
    
    inlet99      <- dat[dat$year == 1999,]
    inlet99.mn   <- round(mean(inlet99$CPUE.SABLE.COUNT/inlet99$CPUE.TRAPS, na.rm=TRUE),0)
    inlet99kg.mn <- round(mean(inlet99$CPUE.SABLE.WEIGHT/inlet99$CPUE.TRAPS, na.rm=TRUE),0)    
    
    inlet18     <- dat[dat$year == yr,]                                     # text for cpue mean year one
    data18.mn   <- round(mean(inlet18$CPUE.SABLE.COUNT/inlet18$CPUE.TRAPS),0)
    data18kg.mn <- round(mean(inlet18$CPUE.SABLE.WEIGHT/inlet18$CPUE.TRAPS),0)
    data18kg    <- round(mean(inlet18$CPUE.SABLE.WEIGHT/inlet18$CPUE.SABLE.COUNT),1)
    
    inlet19     <- dat[dat$year == yr+1,]                                   # text for cpue mean year two
    data19.mn   <- round(mean(inlet19$CPUE.SABLE.COUNT/inlet19$CPUE.TRAPS),0)
    data19kg.mn <- round(mean(inlet19$CPUE.SABLE.WEIGHT/inlet19$CPUE.TRAPS),0)
    data19kg    <- round(mean(inlet19$CPUE.SABLE.WEIGHT/inlet19$CPUE.SABLE.COUNT),1)
    
    #print(data18.mn)
    #print(inlet98.mn)
    
    #print(data19.mn)
    #print(inlet99.mn)
    
```
## CATCH PER UNIT EFFORT (CPUE) 

### Stratified Random CPUE

In general, catch per unit effort as indexed by kilograms (Figure \@ref(fig:figure7)) and numbers (Figure \@ref(fig:figure8)) of sablefish per trap, attained the highest catch rates in the middle depth stratum (RD~2~) in most years. The average weight of sablefish over time in the deep (RD~3~)  and shallow waters (RD~1~) tended to be higher in the northern survey areas. In the middle depths (RD~2~), the mean weights were consistently higher in area S~4~ (Figure \@ref(fig:figure9)).  CPUE over the survey years (2003 to 2011) reached over 30 kg/trap and over 11 fish/trap in 2003 and 2006 (Figure \@ref(fig:figure10),a,b), while the average weight of sablefish remained ~ 3 kg  (Figure \@ref(fig:figure10),c).

### Offshore Indexing CPUE

Standardized sets were conducted at offshore indexing sites from 1988 through 2010. The 1988 and 1989 standardized catch rates were not included in Figure \@ref(fig:figure7) as the fishing protocols were significantly different than future surveys [@Wyeth2003].  The mean catch rates remained high from 1990 through 1993, with the year 1993 yielding the highest mean catch rate. Then, consistent lower catch rates were exhibited from 1994 to 2002, with the year 2001 yielding the lowest mean catch rate. In 2003 and 2004, the mean catch rates were again higher and similar to those in the first couple years in the 1990’s.  The years 2005 through 2010 declined to lower catch rates that resembled those in the late 1990’s and year 2000 (Figure \@ref(fig:figure11),a,b).  The mean sablefish weight remained over 3.0 kg for years 1990 to 2010 with the exception of 1990, 2006 and 2007 (Figure \@ref(fig:figure11),c).

### Mainland Inlet CPUE

CPUE in the mainlaind inlets has varied in a relatively predictable manner over time with peak CPUE occuring every 5-7 years. In the early part of the time series (mid-1990s) average CPUE remained relatively constant before a peak in CPUE was observed in 1999, followed by declines to consistent levels until another peak in 2003 and 2004, and again in 2011 (Figure \@ref(fig:figure12) a,b). Annual mean weights of sablefish over time were less than those at offshore indexing localities (Figure \@ref(fig:figure12) c).

```{r SpeciesCompositionText, echo=FALSE}

 # -- species composition counts for OffShore sets year one
   spc.OffS                <- paste("select dbo.fnIntegerToWords(SUM(CAST(Roundfish as int))) as tRound,  ",
                                "dbo.fnIntegerToWords(SUM(Rockfish))     as tRock,   ",
                                "dbo.fnIntegerToWords(SUM(Flatfish))     as tFlat,   ",
                                "dbo.fnIntegerToWords(SUM(Invertebrate)) as tInvert, ",
                                "dbo.fnIntegerToWords(SUM(Mammal))       as tMammal, ",
                                "dbo.fnIntegerToWords(SUM(Bird))         as tBird,   ",
                                "dbo.fnIntegerToWords(SUM(counter))      as total,    ",
                                "SUM(CAST(Roundfish as int))    as nRound, ",
                                "SUM(CAST(Rockfish as int))     as nRock, ",
                                "SUM(CAST(Flatfish as int))     as nFlat, ",
                                "SUM(CAST(Invertebrate as int)) as nInvert, ",
                                "SUM(CAST(Mammal as int))       as nMammal, ",
                                "SUM(CAST(Bird as int))         as nBird, ",
                                "SUM(CAST(counter as int))      as ntotal ",
                                "from (select case when Fish = Rockfish or Fish = Flatfish then 0 ELSE Fish end AS Roundfish, ",
                                "Fish, Rockfish, Flatfish, Invertebrate, Mammal, Bird, ",
                                "SABLE_SET_TYPE, TRIP_ID, 1 AS counter, Year, SPECIES_CODE from dbo.GFBIO_RESEARCH_CATCH ",
                                "group by ",
                                "Fish, Rockfish, Flatfish, Invertebrate, Mammal, Bird, SABLE_SET_TYPE, Year, TRIP_ID,  ",
                                "case when Fish = Rockfish or Fish = Flatfish then 0 ELSE Fish end, SPECIES_CODE  ",
                                "having (SABLE_SET_TYPE = N'Offshore Standardized') and (Year = ", yr,")) AS RC", sep="")
   #OffS.sp.Comp.yr1    <- GetSQLData(spc.OffS,"Sablefish")
   #write.table(OffS.sp.Comp.yr1 , file = paste(path,"results4a.csv",sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")    
   OffS.sp.Comp.yr1    <-   read.csv(paste(path,'results4a.csv',sep=''),header=T)
   
   roundfish.OffS.count.yr1    <- OffS.sp.Comp.yr1[1,1]
   rockfish.OffS.count.yr1     <- OffS.sp.Comp.yr1[1,2]
   flatfish.OffS.count.yr1     <- OffS.sp.Comp.yr1[1,3]
   invert.OffS.count.yr1       <- OffS.sp.Comp.yr1[1,4]
   mammal.OffS.count.yr1       <- OffS.sp.Comp.yr1[1,5]
   bird.OffS.count.yr1         <- OffS.sp.Comp.yr1[1,6]
   
   # check what is available for paragraph words
   # print(paste(roundfish.OffS.count.yr1,rockfish.OffS.count.yr1,flatfish.OffS.count.yr1,invert.OffS.count.yr1,mammal.OffS.count.yr1,bird.OffS.count.yr1))

   total.OffS.yr1       <- as.character(OffS.sp.Comp.yr1[1,7]) # taxonomic unit count for OffShore Standardized

 # -- species composition counts for StRS sets year one
   spc                <- paste("select dbo.fnIntegerToWords(SUM(CAST(Roundfish as int))) as tRound,  ",
                                "dbo.fnIntegerToWords(SUM(Rockfish))     as tRock,   ",
                                "dbo.fnIntegerToWords(SUM(Flatfish))     as tFlat,   ",
                                "dbo.fnIntegerToWords(SUM(Invertebrate)) as tInvert, ",
                                "dbo.fnIntegerToWords(SUM(Mammal))       as tMammal, ",
                                "dbo.fnIntegerToWords(SUM(Bird))         as tBird,   ",
                                "dbo.fnIntegerToWords(SUM(counter))      as total,    ",
                                "SUM(CAST(Roundfish as int))    as nRound, ",
                                "SUM(CAST(Rockfish as int))     as nRock, ",
                                "SUM(CAST(Flatfish as int))     as nFlat, ",
                                "SUM(CAST(Invertebrate as int)) as nInvert, ",
                                "SUM(CAST(Mammal as int))       as nMammal, ",
                                "SUM(CAST(Bird as int))         as nBird, ",
                                "SUM(CAST(counter as int))      as ntotal ",
                                "from (select case when Fish = Rockfish or Fish = Flatfish then 0 ELSE Fish end AS Roundfish, ",
                                "Fish, Rockfish, Flatfish, Invertebrate, Mammal, Bird, ",
                                "SABLE_SET_TYPE, TRIP_ID, 1 AS counter, Year, SPECIES_CODE from dbo.GFBIO_RESEARCH_CATCH ",
                                "group by ",
                                "Fish, Rockfish, Flatfish, Invertebrate, Mammal, Bird, SABLE_SET_TYPE, Year, TRIP_ID,  ",
                                "case when Fish = Rockfish or Fish = Flatfish then 0 ELSE Fish end, SPECIES_CODE  ",
                                "having (SABLE_SET_TYPE = N'StRS') and (Year = ", yr,")) AS RC", sep="")
   #strs.sp.Comp.yr1    <- GetSQLData(spc,"Sablefish")
   #write.table(strs.sp.Comp.yr1 , file = paste(path,"results4b.csv",sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")    
   strs.sp.Comp.yr1    <-   read.csv(paste(path,'results4b.csv',sep=''),header=T)
   
   roundfish.StRS.count.yr1    <- strs.sp.Comp.yr1[1,1]
   rockfish.StRS.count.yr1     <- strs.sp.Comp.yr1[1,2]
   flatfish.StRS.count.yr1     <- strs.sp.Comp.yr1[1,3]
   invert.StRS.count.yr1       <- strs.sp.Comp.yr1[1,4]
   mammal.StRS.count.yr1       <- strs.sp.Comp.yr1[1,5]
   bird.StRS.count.yr1         <- strs.sp.Comp.yr1[1,6]
   
   # check what is available for paragraph words
   # print(paste(roundfish.StRS.count.yr1,rockfish.StRS.count.yr1,flatfish.StRS.count.yr1,invert.StRS.count.yr1,mammal.StRS.count.yr1,bird.StRS.count.yr1))

   total.StRS.yr1       <- as.character(strs.sp.Comp.yr1[1,7]) # taxonomic unit count for StRS
   
  # -- species composition counts inlet sets year one
   spc.Inlet           <- paste("select dbo.fnIntegerToWords(SUM(CAST(Roundfish AS int))) AS tRound,   ",
                                 "dbo.fnIntegerToWords(ISNULL(SUM(Rockfish),0))     AS tRock, ",
                                 "dbo.fnIntegerToWords(ISNULL(SUM(Flatfish),0))     AS tFlat,    ",
                                 "dbo.fnIntegerToWords(ISNULL(SUM(Invertebrate),0)) AS tInvert,  ",
                                 "dbo.fnIntegerToWords(ISNULL(SUM(Mammal),0))       AS tMammal,  ",
                                 "dbo.fnIntegerToWords(ISNULL(SUM(Bird),0))         AS tBird,    ",
                                 "dbo.fnIntegerToWords(SUM(counter))                AS total,     ",
                                 "SUM(CAST(Roundfish as int))    as nRound, ",
                                 "SUM(CAST(Rockfish as int))     as nRock, ",
                                 "SUM(CAST(Flatfish as int))     as nFlat, ",
                                 "SUM(CAST(Invertebrate as int)) as nInvert, ",
                                 "SUM(CAST(Mammal as int))       as nMammal, ",
                                 "SUM(CAST(Bird as int))         as nBird, ",
                                 "SUM(CAST(counter as int))      as ntotal ",
                                 "from   (select CASE WHEN Fish = Rockfish or Fish = Flatfish THEN 0 ELSE Fish END AS Roundfish,  ",
                                 "Fish, Rockfish, Flatfish, Invertebrate, Mammal, Bird,       ",
                                 "SABLE_SET_TYPE, TRIP_ID, 1 AS counter, Year, SPECIES_CODE   ",
                                 "from dbo.GFBIO_RESEARCH_CATCH  ",
                                 "group by Fish, Rockfish, Flatfish, Invertebrate, Mammal, Bird, SABLE_SET_TYPE, Year, TRIP_ID, ",
                                 "CASE WHEN Fish = Rockfish or Fish = Flatfish THEN 0 ELSE Fish END, SPECIES_CODE ",
                                 "having (SABLE_SET_TYPE = N'INLET STANDARDIZED')       ",
                                 "and (Year = ",yr,")) AS RC",sep="")
   #inlet.sp.Comp.yr1    <- GetSQLData(spc.Inlet,"Sablefish")
   #write.table(inlet.sp.Comp.yr1, file = paste(path,"results5.csv",sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")    
   inlet.sp.Comp.yr1    <- read.csv(paste(path,'results5.csv',sep=''),header=T)
    
   roundfish.Inlet.count.yr1   <- inlet.sp.Comp.yr1[1,1]
   rockfish.Inlet.count.yr1    <- inlet.sp.Comp.yr1[1,2]
   flatfish.Inlet.count.yr1    <- inlet.sp.Comp.yr1[1,3]
   invert.Inlet.count.yr1      <- inlet.sp.Comp.yr1[1,4]
   mammal.Inlet.count.yr1      <- inlet.sp.Comp.yr1[1,5]
   bird.Inlet.count.yr1        <- inlet.sp.Comp.yr1[1,6]
   
   # check what is available for paragraph words
   # print(paste(roundfish.Inlet.count.yr1,rockfish.Inlet.count.yr1,flatfish.Inlet.count.yr1,invert.Inlet.count.yr1,mammal.Inlet.count.yr1,bird.Inlet.count.yr1))
   
   total.Inlet.yr1       <- as.character(inlet.sp.Comp.yr1[1,7])               # taxonomic units count for inlets

  # -- taxonomic top 3 group count Offshore Standardized year one
   topOffS      <- paste("select top (3) SPECIES_COMMON_NAME, SPECIES_SCIENCE_NAME, ",
                         "sum(CATCH_WEIGHT) AS catchkg ",
                         "from dbo.GFBIO_RESEARCH_CATCH ",
                         "group by SABLE_SET_TYPE, Year, SPECIES_CODE, ",
                         "SPECIES_COMMON_NAME, SPECIES_SCIENCE_NAME ",
                         "having (SABLE_SET_TYPE = N'OFFSHORE STANDARDIZED') and ",
                         "(SPECIES_CODE <> N'455') and (Year = ",yr,") ",
                         "order by catchkg DESC", sep="") 
   #top.OffS.species    <- GetSQLData(topOffS ,"Sablefish") 
  # write.table(top.OffS.species, file = paste(path,"results2a.csv",sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")    
   top.OffS.species  <-  read.csv(paste(path,'results2a.csv',sep=''),header=T)
   
   top.OffS.sp1.yr1   <- tolower(as.character(top.OffS.species[1,1]))                    # -- OffShore top 3 species names
   top.OffS.sp1.yr1   <- gsub("pacific","Pacific", top.OffS.sp1.yr1)                    # -- capital on Pacific if it occurs
   top.OffS.science1.yr1   <- firstup(tolower(as.character(top.OffS.species[1,2])))      # -- OffShore top 3 species science names
   
   top.OffS.sp2.yr1   <- as.character(top.OffS.species[2,1]) 
   top.OffS.sp2.yr1   <- gsub("pacific","Pacific", top.OffS.sp2.yr1)                              
   top.OffS.science2.yr1   <- firstup(tolower(as.character(top.OffS.species[2,2])))   
   
   top.OffS.sp3.yr1   <- tolower(as.character(top.OffS.species[3,1])) 
   top.OffS.sp3.yr1   <- gsub("pacific","Pacific", top.OffS.sp3.yr1)
   top.OffS.science3.yr1   <- firstup(tolower(as.character(top.OffS.species[3,2])))
   top.OffS.science3.yr1   <- gsub("Sebastes aleutianus","Sebastes aleutianus/melanostictus", top.OffS.science3.yr1) 
   
   # review results
   # print(paste(top.OffS.sp1.yr1,top.OffS.science1.yr1,top.OffS.sp2.yr1,top.OffS.science2.yr1,top.OffS.sp3.yr1,top.OffS.science3.yr1,sep=","))
   
   
  # -- taxonomic top 5 group count StRS year one
   topStRS      <- paste("select top (5) SPECIES_COMMON_NAME, SPECIES_SCIENCE_NAME, ",
                         "sum(CATCH_WEIGHT) AS catchkg ",
                         "from dbo.GFBIO_RESEARCH_CATCH ",
                         "group by SABLE_SET_TYPE, Year, SPECIES_CODE, ",
                         "SPECIES_COMMON_NAME, SPECIES_SCIENCE_NAME ",
                         "having (SABLE_SET_TYPE = N'StRS') and ",
                         "(SPECIES_CODE <> N'455') and (Year = ",yr,") ",
                         "order by catchkg DESC", sep="") 
   #topStRS.species    <- GetSQLData(topStRS,"Sablefish") 
   #write.table(topStRS.species, file = paste(path,"results2b.csv",sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")    
   topStRS.species  <-  read.csv(paste(path,'results2b.csv',sep=''),header=T)
   
   
   top.StRS.sp1.yr1   <- tolower(as.character(topStRS.species[1,1]))                    # -- StRS top 5 species names
   top.StRS.sp1.yr1   <- gsub("pacific","Pacific", top.StRS.sp1.yr1)                    # -- capital on Pacific if it occurs
   top.StRS.science1.yr1   <- firstup(tolower(as.character(topStRS.species[1,2])))      # -- StRS top 5 species science names
   
   top.StRS.sp2.yr1   <- tolower(as.character(topStRS.species[2,1]) )
   top.StRS.sp2.yr1   <- gsub("pacific","Pacific", top.StRS.sp2.yr1)                              
   top.StRS.science2.yr1   <- firstup(tolower(as.character(topStRS.species[2,2])))   
   
   top.StRS.sp3.yr1   <- tolower(as.character(topStRS.species[3,1])) 
   top.StRS.sp3.yr1   <- gsub("pacific","Pacific", top.StRS.sp3.yr1)  
   top.StRS.science3.yr1   <- firstup(tolower(as.character(topStRS.species[3,2])))
   
   top.StRS.sp4.yr1   <- tolower(as.character(topStRS.species[4,1]) )
   top.StRS.sp4.yr1   <- gsub("pacific","Pacific", top.StRS.sp4.yr1)    
   top.StRS.science4.yr1   <- firstup(tolower(as.character(topStRS.species[4,2])))  
   
   top.StRS.sp5.yr1   <- tolower(as.character(topStRS.species[5,1]))     
   top.StRS.sp5.yr1   <- gsub("pacific","Pacific", top.StRS.sp5.yr1)    
   top.StRS.science5.yr1   <- firstup(tolower(as.character(topStRS.species[5,2]))) 
   
   # review results
   # print(paste(top.StRS.sp1.yr1,top.StRS.science1.yr1,top.StRS.sp2.yr1,top.StRS.science2.yr1,top.StRS.sp3.yr1,
             #  top.StRS.science3.yr1,top.StRS.sp4.yr1,top.StRS.science4.yr1,top.StRS.sp5.yr1,top.StRS.science5.yr1,sep=","))

  # -- taxonomic group count Inlets year one
   topInlet     <- paste("select top (2) SPECIES_COMMON_NAME, SPECIES_SCIENCE_NAME, sum(CATCH_WEIGHT) AS catchkg
                          from dbo.GFBIO_RESEARCH_CATCH 
                          group by SABLE_SET_TYPE, Year, SPECIES_CODE, SPECIES_COMMON_NAME, SPECIES_SCIENCE_NAME
                          having (SABLE_SET_TYPE = N'INLET STANDARDIZED') and (SPECIES_CODE <> N'455') and (Year = ",yr,")
                          order by catchkg DESC", sep="") 
   
   #top.Inlet.sp   <- GetSQLData(topInlet,"Sablefish")   
   #write.table(top.Inlet.sp , file = paste(path,"results3.csv",sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")       
   top.Inlet.sp   <- read.csv(paste(path,'results3.csv',sep=''),header=T)

   top.Inlet.sp1.yr1  <- tolower(as.character(top.Inlet.sp[1,1]))    # -- inlet top 2 species names
   top.Inlet.sp1.yr1   <- gsub("pacific","Pacific", top.Inlet.sp1.yr1)
   top.Inlet.science1.yr1  <- firstup(tolower(as.character(top.Inlet.sp[1,2])))  # -- inlet top 2 species science names
   
   top.Inlet.sp2.yr1  <- tolower(as.character(top.Inlet.sp[2,1]))
   top.Inlet.sp2.yr1   <- gsub("pacific","Pacific", top.Inlet.sp2.yr1)
   top.Inlet.science2.yr1  <- firstup(tolower(as.character(top.Inlet.sp[2,2]))) 
   
   # review results
   # print(paste(top.Inlet.sp1.yr1, top.Inlet.science1.yr1,top.Inlet.sp2.yr1, top.Inlet.science2.yr1, sep=","))
   
  
   
```
## CATCH COMPOSITION

### 2010 Survey

A total of `r total.StRS.yr1[1]` (`r strs.sp.Comp.yr1$ntotal`) taxonomic groups were represented in the catches in StRS sets in `r yr[1]` (Table \@ref(tab:Table3)).  These included `r roundfish.StRS.count.yr1[1]` (`r strs.sp.Comp.yr1$nRound`) roundfish species, `r rockfish.StRS.count.yr1[1]` (`r strs.sp.Comp.yr1$nRock`) rockfish species, `r flatfish.StRS.count.yr1[1]`  (`r strs.sp.Comp.yr1$nFlat`) flatfish species and `r invert.StRS.count.yr1[1]` (`r strs.sp.Comp.yr1$nInvert`) invertebrate species. Other than sablefish, the most common species, by weight,  were  `r top.StRS.sp1.yr1` (*`r top.StRS.science1.yr1`*), `r top.StRS.sp2.yr1` (*`r top.StRS.science2.yr1`*) and `r top.StRS.sp3.yr1` (*`r top.StRS.science3.yr1`*).

A total of `r total.OffS.yr1` (`r OffS.sp.Comp.yr1$ntotal`) taxonomic groups were represented in the catches in standardized sets at offshore localities in `r yr[1]` (Table \@ref(tab:Table4)).  These included `r roundfish.OffS.count.yr1[1]` (`r OffS.sp.Comp.yr1$nRound`) roundfish species, `r rockfish.OffS.count.yr1[1]` (`r OffS.sp.Comp.yr1$nRock`) rockfish species, `r flatfish.OffS.count.yr1[1]`  (`r OffS.sp.Comp.yr1$nFlat`) flatfish species and `r invert.OffS.count.yr1[1]` (`r OffS.sp.Comp.yr1$nInvert`) invertebrate species. Other than sablefish, the most common species, by weight,  were  `r top.OffS.sp1.yr1` (*`r top.OffS.science1.yr1`*), `r top.OffS.sp2.yr1` (*`r top.OffS.science2.yr1`*) and `r top.OffS.sp3.yr1` (*`r top.OffS.science3.yr1`*).

A total of `r total.Inlet.yr1` (`r inlet.sp.Comp.yr1$ntotal`) taxonomic groups were represented in the catches from traditional standardized sets conducted in mainland inlet localities in `r yr[1]` (Table \@ref(tab:Table5)).  These included `r roundfish.Inlet.count.yr1` (`r inlet.sp.Comp.yr1$nRound`) roundfish species, `r rockfish.Inlet.count.yr1` (`r inlet.sp.Comp.yr1$nRock`) rockfish species, `r flatfish.Inlet.count.yr1` (`r inlet.sp.Comp.yr1$nFlat`) flatfish species and `r invert.Inlet.count.yr1` (`r inlet.sp.Comp.yr1$nInvert`) invertebrate species.  The most common species captured, in order of total weights, other than sablefish were `r top.Inlet.sp1.yr1` (*`r top.Inlet.science1.yr1`*) and  `r top.Inlet.sp2.yr1` (*`r top.Inlet.science2.yr1`*). 

```{r SpeciesCompositionYear2, echo=FALSE}

 # -- species composition counts for StRS sets year two
   spc                <- paste("select dbo.fnIntegerToWords(SUM(CAST(Roundfish as int))) as tRound,  ",
                                "dbo.fnIntegerToWords(SUM(Rockfish))     as tRock,   ",
                                "dbo.fnIntegerToWords(SUM(Flatfish))     as tFlat,   ",
                                "dbo.fnIntegerToWords(SUM(Invertebrate)) as tInvert, ",
                                "dbo.fnIntegerToWords(SUM(Mammal))       as tMammal, ",
                                "dbo.fnIntegerToWords(SUM(Bird))         as tBird,   ",
                                "dbo.fnIntegerToWords(SUM(counter))      as total,    ",
                                "SUM(CAST(Roundfish as int))    as nRound, ",
                                "SUM(CAST(Rockfish as int))     as nRock, ",
                                "SUM(CAST(Flatfish as int))     as nFlat, ",
                                "SUM(CAST(Invertebrate as int)) as nInvert, ",
                                "SUM(CAST(Mammal as int))       as nMammal, ",
                                "SUM(CAST(Bird as int))         as nBird, ",
                                "SUM(CAST(counter as int))      as ntotal ",
                                "from (select case when Fish = Rockfish or Fish = Flatfish then 0 ELSE Fish end AS Roundfish, ",
                                "Fish, Rockfish, Flatfish, Invertebrate, Mammal, Bird, ",
                                "SABLE_SET_TYPE, TRIP_ID, 1 AS counter, Year, SPECIES_CODE from dbo.GFBIO_RESEARCH_CATCH ",
                                "group by ",
                                "Fish, Rockfish, Flatfish, Invertebrate, Mammal, Bird, SABLE_SET_TYPE, Year, TRIP_ID,  ",
                                "case when Fish = Rockfish or Fish = Flatfish then 0 ELSE Fish end, SPECIES_CODE  ",
                                "having (SABLE_SET_TYPE = N'StRS') and (Year = ", yr+1,")) AS RC", sep="")
   #strs.sp.Comp.yr2  <- GetSQLData(spc,"Sablefish")
   #write.table(strs.sp.Comp.yr2 , file = paste(path,"results8.csv",sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")    
   strs.sp.Comp.yr2   <-   read.csv(paste(path,'results8.csv',sep=''),header=T)
   
   roundfish.StRS.count.yr2   <- strs.sp.Comp.yr2[1,1]
   rockfish.StRS.count.yr2    <- strs.sp.Comp.yr2[1,2]
   flatfish.StRS.count.yr2    <- strs.sp.Comp.yr2[1,3]
   invert.StRS.count.yr2      <- strs.sp.Comp.yr2[1,4]
   mammal.StRS.count.yr2      <- strs.sp.Comp.yr2[1,5]
   bird.StRS.count.yr2        <- strs.sp.Comp.yr2[1,6]
   
   # check what is available for paragraph words
   # print(paste(roundfish.StRS.count.yr2,rockfish.StRS.count.yr2,flatfish.StRS.count.yr2,invert.StRS.count.yr2,mammal.StRS.count.yr2,bird.StRS.count.yr2))

   total.StRS.yr2             <- as.character(strs.sp.Comp.yr2[1,7]) # taxonomic unit count for StRS
   
  # -- species composition counts inlet sets year two
   spc.Inlet           <- paste("select dbo.fnIntegerToWords(SUM(CAST(Roundfish AS int))) AS tRound,   ",
                                 "dbo.fnIntegerToWords(ISNULL(SUM(Rockfish),0))     AS tRock, ",
                                 "dbo.fnIntegerToWords(ISNULL(SUM(Flatfish),0))     AS tFlat,    ",
                                 "dbo.fnIntegerToWords(ISNULL(SUM(Invertebrate),0)) AS tInvert,  ",
                                 "dbo.fnIntegerToWords(ISNULL(SUM(Mammal),0))       AS tMammal,  ",
                                 "dbo.fnIntegerToWords(ISNULL(SUM(Bird),0))         AS tBird,    ",
                                 "dbo.fnIntegerToWords(SUM(counter))                AS total,     ",  
                                 "SUM(CAST(Roundfish as int))    as nRound, ",
                                 "SUM(CAST(Rockfish as int))     as nRock, ",
                                 "SUM(CAST(Flatfish as int))     as nFlat, ",
                                 "SUM(CAST(Invertebrate as int)) as nInvert, ",
                                 "SUM(CAST(Mammal as int))       as nMammal, ",
                                 "SUM(CAST(Bird as int))         as nBird, ",
                                 "SUM(CAST(counter as int))      as ntotal ",
                                 "from (select CASE WHEN Fish = Rockfish or Fish = Flatfish THEN 0 ELSE Fish END AS Roundfish,  ",
                                 "Fish, Rockfish, Flatfish, Invertebrate, Mammal, Bird,       ",
                                 "SABLE_SET_TYPE, TRIP_ID, 1 AS counter, Year, SPECIES_CODE   ",
                                 "from dbo.GFBIO_RESEARCH_CATCH  ",
                                 "group by Fish, Rockfish, Flatfish, Invertebrate, Mammal, Bird, SABLE_SET_TYPE, Year, TRIP_ID, ",
                                 "CASE WHEN Fish = Rockfish or Fish = Flatfish THEN 0 ELSE Fish END, SPECIES_CODE ",
                                 "having (SABLE_SET_TYPE = N'INLET STANDARDIZED')       ",
                                 "and (Year = ", yr + 1,")) AS RC", sep="")
   #inlet.sp.Comp.yr2    <- GetSQLData(spc.Inlet,"Sablefish")
   #write.table(inlet.sp.Comp.yr2, file = paste(path,"results9.csv",sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")    
   inlet.sp.Comp.yr2     <- read.csv(paste(path,'results9.csv',sep=''),header=T)
    
   roundfish.Inlet.count.yr2   <- inlet.sp.Comp.yr2[1,1]
   rockfish.Inlet.count.yr2    <- inlet.sp.Comp.yr2[1,2]
   flatfish.Inlet.count.yr2    <- inlet.sp.Comp.yr2[1,3]
   invert.Inlet.count.yr2      <- inlet.sp.Comp.yr2[1,4]
   mammal.Inlet.count.yr2      <- inlet.sp.Comp.yr2[1,5]
   bird.Inlet.count.yr2        <- inlet.sp.Comp.yr2[1,6]
   
   # check what is available for paragraph words
   # print(paste(roundfish.Inlet.count.yr2,rockfish.Inlet.count.yr2,flatfish.Inlet.count.yr2,invert.Inlet.count.yr2,mammal.Inlet.count.yr2,bird.Inlet.count.yr2))
   
   total.Inlet.yr2       <- firstup(as.character(inlet.sp.Comp.yr2[1,7]))       # taxonomic units count for inlets with capital
   total.Inlet.yr2       <- as.character(inlet.sp.Comp.yr2[1,7])                # taxonomic units count for inlets

   # -- taxonomic top 5 group count StRS year two
   topStRS      <- paste("select top (5) SPECIES_COMMON_NAME, SPECIES_SCIENCE_NAME, ",
                         "sum(CATCH_WEIGHT) AS catchkg ",
                         "from dbo.GFBIO_RESEARCH_CATCH ",
                         "group by SABLE_SET_TYPE, Year, SPECIES_CODE, ",
                         "SPECIES_COMMON_NAME, SPECIES_SCIENCE_NAME ",
                         "having (SABLE_SET_TYPE = N'StRS') and ",
                         "(SPECIES_CODE <> N'455') and (Year = ",yr +1,") ",
                         "order by catchkg DESC", sep="") 
   #topStRS.species    <- GetSQLData(topStRS,"Sablefish") 
   #write.table(topStRS.species, file = paste(path,"results6.csv",sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")    
   topStRS.species  <-  read.csv(paste(path,'results6.csv',sep=''),header=T)
   
   
   top.StRS.sp1.yr2   <- tolower(as.character(topStRS.species[1,1]))                    # -- StRS top 5 species names
   top.StRS.sp1.yr2   <- gsub("pacific","Pacific", top.StRS.sp1.yr2)                    # -- capital on Pacific if it occurs
   top.StRS.science1.yr2   <- firstup(tolower(as.character(topStRS.species[1,2])))      # -- StRS top 5 species science names
   
   top.StRS.sp2.yr2   <- tolower(as.character(topStRS.species[2,1]))
   top.StRS.sp2.yr2   <- gsub("pacific","Pacific", top.StRS.sp2.yr2)                              
   top.StRS.science2.yr2   <- firstup(tolower(as.character(topStRS.species[2,2])))   
   
   top.StRS.sp3.yr2   <- tolower(as.character(topStRS.species[3,1])) 
   top.StRS.sp3.yr2   <- gsub("pacific","Pacific", top.StRS.sp3.yr2)  
   top.StRS.science3.yr2   <- firstup(tolower(as.character(topStRS.species[3,2])))
   
   top.StRS.sp4.yr2   <- tolower(as.character(topStRS.species[4,1]) )
   top.StRS.sp4.yr2   <- gsub("pacific","Pacific", top.StRS.sp4.yr2)    
   top.StRS.science4.yr2   <- firstup(tolower(as.character(topStRS.species[4,2])))  
   
   top.StRS.sp5.yr2   <- tolower(as.character(topStRS.species[5,1]))     
   top.StRS.sp5.yr2   <- gsub("pacific","Pacific", top.StRS.sp5.yr2)    
   top.StRS.science5.yr2   <- firstup(tolower(as.character(topStRS.species[5,2]))) 
   
   # review results
   # print(paste(top.StRS.sp1.yr2,top.StRS.science1.yr2,top.StRS.sp2.yr2,top.StRS.science2.yr2,top.StRS.sp3.yr2,
             #  top.StRS.science3.yr2,top.StRS.sp4.yr2,top.StRS.science4.yr2,top.StRS.sp5.yr2,top.StRS.science5.yr2,sep=","))

  # -- taxonomic group count Inlets year one
   topInlet     <- paste("select top (2) SPECIES_COMMON_NAME, SPECIES_SCIENCE_NAME, sum(CATCH_WEIGHT) AS catchkg
                          from dbo.GFBIO_RESEARCH_CATCH 
                          group by SABLE_SET_TYPE, Year, SPECIES_CODE, SPECIES_COMMON_NAME, SPECIES_SCIENCE_NAME
                          having (SABLE_SET_TYPE = N'INLET STANDARDIZED') and (SPECIES_CODE <> N'455') and (Year = ",yr +1,")
                          order by catchkg DESC", sep="") 
   
   #top.Inlet.sp   <- GetSQLData(topInlet,"Sablefish")   
   #write.table(top.Inlet.sp , file = paste(path,"results7.csv",sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")       
   top.Inlet.sp   <- read.csv(paste(path,'results7.csv',sep=''),header=T)

   top.Inlet.sp1.yr2  <- tolower(as.character(top.Inlet.sp[1,1]))    # -- inlet top 2 species names
   top.Inlet.sp1.yr2   <- gsub("pacific","Pacific", top.Inlet.sp1.yr2)
   top.Inlet.science1.yr2  <- firstup(tolower(as.character(top.Inlet.sp[1,2])))  # -- inlet top 2 species science names
   
   top.Inlet.sp2.yr2  <- tolower(as.character(top.Inlet.sp[2,1]))
   top.Inlet.sp2.yr2   <- gsub("pacific","Pacific", top.Inlet.sp2.yr2)
   top.Inlet.science2.yr2  <- firstup(tolower(as.character(top.Inlet.sp[2,2]))) 
   
   # review results
   # print(paste(top.Inlet.sp1.yr2, top.Inlet.science1.yr2,top.Inlet.sp2.yr2, top.Inlet.science2.yr2, sep=","))

```
### 2011 Survey

A total of `r total.StRS.yr2[1]` (`r strs.sp.Comp.yr2$ntotal`) taxonomic groups were represented in StRS sets in `r yr+1` (Table \@ref(tab:Table6)).  These included `r roundfish.StRS.count.yr2[1]` (`r strs.sp.Comp.yr2$nRound`) roundfish species, `r rockfish.StRS.count.yr2[1]` (`r strs.sp.Comp.yr2$nRock`) rockfish species, `r flatfish.StRS.count.yr2[1]` (`r strs.sp.Comp.yr2$nFlat`) flatfish species and `r invert.StRS.count.yr2[1]` (`r strs.sp.Comp.yr2$nInvert`) invertebrate species. Other than sablefish, the most common species, by weight, were `r top.StRS.sp1.yr2[1]` (*`r top.StRS.science1.yr2`*), `r top.StRS.sp2.yr2` (*`r top.StRS.science2.yr2`*) and `r top.StRS.sp3.yr2` (*`r top.StRS.science3.yr2`*). 

A total of `r total.Inlet.yr2` (`r inlet.sp.Comp.yr2$ntotal`) taxonomic groups were represented in the catches from traditional standardized sets conducted in mainland inlet localities in `r yr+1` (Table \@ref(tab:Table7)).  These included `r roundfish.Inlet.count.yr2 ` (`r inlet.sp.Comp.yr2$nRound`) roundfish species, `r rockfish.Inlet.count.yr2 ` (`r inlet.sp.Comp.yr2$nRock`)  rockfish species, `r flatfish.Inlet.count.yr2 ` (`r inlet.sp.Comp.yr2$nFlat`) flatfish species and `r invert.Inlet.count.yr2 ` (`r inlet.sp.Comp.yr2$nInvert`) invertebrate species.  The most common species, by weight, other than sablefish were `r top.Inlet.sp1.yr2` (*`r top.Inlet.science1.yr2`*) and `r top.Inlet.sp2.yr2` (*`r top.Inlet.science2.yr2`*).

A total of eighteen (18) taxonomic groups were represented in the catches from  sets conducted in exploratory sites in 2011 (Table \@ref(tab:Table8)). These included six (6) roundfish species, four (4) rockfish species, three (3) flatfish species and five (5) invertebrate species. The most common species by weight were lingcod (*Ophiodon elongatus*) and spiny dogfish (*Squalus acanthia*).


```{r SamplingWords, echo=FALSE}
    # inline text query Sablefish.dbo.GFBIO_RESEARCH_SAMPLE_DETAILS for the counts of Sablefish from all sets
    sample.yr1 <- paste("select rt.SABLE_SET_TYPE, ",
                         "SUM(sd.[Total Count])                           AS count, ",
                         "SUM(sd.[Recovered Number])                      AS tagagainlive, ",
                         "SUM(sd.[Recovered Dead Number])                 AS tagdead, ",
                         "SUM(sd.[Tagged Number] + sd.[Recovered Number]) AS tagrelease, " ,
                         "SUM(sd.[Fork Len Tag Sample Count])             AS taglengthsample,  " ,
                         "SUM(sd.Sample_count)                            AS samplecount " ,
                         "from dbo.GFBIO_RESEARCH_SAMPLE_DETAILS AS sd INNER JOIN " ,         
                         "dbo.GFBIO_SABLEBIO_TRIP_SET AS rt ON " ,
                         "sd.TRIP_ID = rt.TRIP_ID AND  sd.[SET] = rt.SET_NUMBER " ,
                         "where (sd.Year =", yr,") group by rt.SABLE_SET_TYPE", sep="")
    #count.sample.yr1   <- GetSQLData(sample.yr1,"Sablefish")
    #write.table(count.sample.yr1 , file = paste(path,"results10.csv", sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")    
    count.sample.yr1    <-  read.csv(paste(path,'results10.csv', sep=''), header=T) 

     # --  StRS year one by spatial and depth strata:  count/mean of samples for fork length and tagged fish fork lengths
     bioStRS      <-   paste(" select locality, depth, PropMales, PropFemales, ",
                         " MalesMnFkLen, FemalesMnFkLen, TaggedMnFkLen ",
                         " from gfbio_sable_bio_summary ",
                         " where  (Depth IN (N'RD1', N'RD2', N'RD3')) and (year = ", yr,
                         " ) order by Locality,Depth", sep="")
     #biosumm  <-   GetSQLData(bioStRS,"Sablefish")
     #write.table(biosumm, file = paste(path,'results13.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",") 
     biosumm   <-    read.csv(paste(path,'results13.csv',sep=''),header=T)      

     colnames(biosumm) <-  c("Spatial","Depth","Males","Females","Males","Females","Tagged")
     biosumm$Spatial   <-  cleanf(biosumm$Spatial)  # use the remove duplicates function

     #  -- sum the count of length values for the table columns
     biosumm[16,3]     <-  round((biosumm[1,3] + biosumm[2,3] + biosumm[3,3])/ 3, 2)  # --  males S1 average proportions
     biosumm[16,4]     <-  round((biosumm[1,4] + biosumm[2,4] + biosumm[3,4])/ 3, 2)  # --  females S1 average proportions
     biosumm[16,5]     <-  round((biosumm[1,5] + biosumm[2,5] + biosumm[3,5])/ 3, 0)  # --  males S1 average fork len
     biosumm[16,6]     <-  round((biosumm[1,6] + biosumm[2,6] + biosumm[3,6])/ 3, 0)  # --  females S1 average fork len 
     biosumm[16,7]     <-  round((biosumm[1,7] + biosumm[2,7] + biosumm[3,7])/ 3, 0)  # --  tagged S1 average fork len
      
     biosumm[17,3]     <-  round((biosumm[4,3] + biosumm[5,3] + biosumm[6,3])/ 3, 2)   # -- S2
     biosumm[17,4]     <-  round((biosumm[4,4] + biosumm[5,4] + biosumm[6,4])/ 3, 2)
     biosumm[17,5]     <-  round((biosumm[4,5] + biosumm[5,5] + biosumm[6,5])/ 3, 0)
     biosumm[17,6]     <-  round((biosumm[4,6] + biosumm[5,6] + biosumm[6,6])/ 3, 0)
     biosumm[17,7]     <-  round((biosumm[4,7] + biosumm[5,7] + biosumm[6,7])/ 3, 0)
      
     biosumm[18,3]     <-  round((biosumm[7,3] + biosumm[8,3] + biosumm[9,3])/ 3, 2)   # -- S3
     biosumm[18,4]     <-  round((biosumm[7,4] + biosumm[8,4] + biosumm[9,4])/ 3, 2)
     biosumm[18,5]     <-  round((biosumm[7,5] + biosumm[8,5] + biosumm[9,5])/ 3, 0)
     biosumm[18,6]     <-  round((biosumm[7,6] + biosumm[8,6] + biosumm[9,6])/ 3, 0)
     biosumm[18,7]     <-  round((biosumm[7,7] + biosumm[8,7] + biosumm[9,7])/ 3, 0)
      
     biosumm[19,3]     <-  round((biosumm[10,3] + biosumm[11,3] + biosumm[12,3])/ 3, 2)  # -- S4
     biosumm[19,4]     <-  round((biosumm[10,4] + biosumm[11,4] + biosumm[12,4])/ 3, 2)
     biosumm[19,5]     <-  round((biosumm[10,5] + biosumm[11,5] + biosumm[12,5])/ 3, 0)
     biosumm[19,6]     <-  round((biosumm[10,6] + biosumm[11,6] + biosumm[12,6])/ 3, 0) 
     biosumm[19,7]     <-  round((biosumm[10,7] + biosumm[11,7] + biosumm[12,7])/ 3, 0) 
      
     biosumm[20,3]     <-  round((biosumm[13,3] + biosumm[14,3] + biosumm[15,3])/ 3, 2)  # --S5
     biosumm[20,4]     <-  round((biosumm[13,4] + biosumm[14,4] + biosumm[15,4])/ 3, 2)
     biosumm[20,5]     <-  round((biosumm[13,5] + biosumm[14,5] + biosumm[15,5])/ 3, 0)
     biosumm[20,6]     <-  round((biosumm[13,6] + biosumm[14,6] + biosumm[15,6])/ 3, 0)  
     biosumm[20,7]     <-  round((biosumm[13,7] + biosumm[14,7] + biosumm[15,7])/ 3, 0)
      
     newdata           <-  rbind(biosumm[1:3,],   biosumm[16,], biosumm[4:6,],  biosumm[17,],
                                 biosumm[7:9,],   biosumm[18,], biosumm[10:12,],biosumm[19,], 
                                 biosumm[13:15,], biosumm[20,])   # r bind the average column results
     
     #newdata$Spatial   <-  cleanf(newdata$Spatial)
     #colnames(newdata) <-  c("Spatial","Depth","Males","Females","Males","Females","Tagged")
     
     pdiffS1 <- biosumm[16,3] - biosumm[16,4]  # --  S1 check male - female prop
     pS1     <- sum(pdiffS1 < 0.00)
     if (pS1 == 1)  {wS1="S~1~, "} else {wS1=""} # --  if value negative, more females
      
     pdiffS2 <- biosumm[17,3] - biosumm[17,4]  #  -- S2 check male - female prop
     pS2 <- sum(pdiffS2 < 0.00)
     if (pS2 == 1)  {wS2="S~2~, "} else {wS2=""} 
      
     pdiffS3 <- biosumm[18,3] - biosumm[18,4]   # --  S3 check male - female prop
     pS3 <- sum(pdiffS3 < 0.00)
     if (pS3 == 1)  {wS3="S~3~, "} else {wS3=""}
      
     pdiffS4 <- biosumm[19,3] - biosumm[19,4]  # -- S4 check male - female prop
     pS4 <- sum(pdiffS4 < 0.00)
     if (pS4 == 1)  {wS4="S~4~, "} else {wS4=""}
      
     pdiffS5 <- biosumm[20,3] - biosumm[20,4]  # -- S4 check male - female prop
     pS5 <- sum(pdiffS5 < 0.00)
     if (pS5 == 1)  {wS5="S~5~, "} else {wS5=""}
      
     stratafem    <- paste(wS1,wS2,wS3,wS4,wS5,sep="")         # -- list of S areas where more females
     stratafema   <- substr(stratafem, 1, nchar(stratafem)-2)  # -- trim trailing comma
     stratafemale <- sub(",([^,]*)$", " and\\1", stratafema)   # -- replace last comma with and
    
     #  More females than males were seen in the shallow depth stratum as per yearly trend...
     shallS1 <- sum((biosumm[1,3] - biosumm[1,4])<0.00)
     
     if (shallS1 == 1)  {shallwS1="S~1~, "} else {shallwS1=""}
           shallS2 <- sum((biosumm[4,3] - biosumm[4,4])<0.00)
           
     if (shallS2 == 1)  {shallwS2="S~2~, "} else {shallwS2=""}
           shallS3 <- sum((biosumm[7,3] - biosumm[7,4])<0.00)
            
     if (shallS3 == 1)  {shallwS3="S~3~, "} else {shallwS3=""}      
           shallS4 <- sum((biosumm[10,3] - biosumm[10,4])<0.00)
            
     if (shallS4 == 1)  {shallwS4="S~4~, "} else {shallwS4=""}  
           shallS5 <- sum((biosumm[13,3] - biosumm[13,4])<0.00)
            
     if (shallS5 == 1)  {shallwS5="S~5~, "} else {shallwS5=""}
            
     shallsfem    <- paste(shallwS1,shallwS2,shallwS3,shallwS4,shallwS5,sep="")
     shallsfema   <- substr(shallsfem, 1, nchar(shallsfem)-2)  # -- trim trailing comma
     shallsfemale <- sub(",([^,]*)$", " and\\1", shallsfema)   # replace last comma with and
     
     # -- Assumption that more males than females were seen in the mid depth stratum
     midS1 <- sum((biosumm[2,3] - biosumm[2,4])>0.00)
      
      if (midS1 == 1)  {midwS1="S~1~, "} else {midwS1=""}
          midS2 <- sum((biosumm[5,3] - biosumm[5,4])>0.00)
      
      if (midS2 == 1)  {midwS2="S~2~, "} else {midwS2=""}
            midS3 <- sum((biosumm[8,3] - biosumm[8,4])>0.00)
      
      if (midS3 == 1)  {midwS3="S~3~, "} else {midwS3=""}      
          midS4 <- sum((biosumm[11,3] - biosumm[11,4])>0.00)
      
      if (midS4 == 1)  {midwS4="S~4~, "} else {midwS4=""}  
            midS5 <- sum((biosumm[14,3] - biosumm[14,4])>0.00)
      
      if (midS5 == 1)  {midwS5="S~5~, "} else {midwS5=""}
            
      midsm    <- paste(midwS1,midwS2,midwS3,midwS4,midwS5,sep="")
      midsma   <- substr(midsm, 1, nchar(midsm)-2)      # -- trim trailing comma
      midsmale <- sub(",([^,]*)$", " and\\1", midsma)   # -- replace last comma with and
      
      # -- Assumption that more females than males were seen in the deep depth stratum
      deepS1 <- sum((biosumm[3,3] - biosumm[3,4])<0.00)
      if (deepS1 == 1)  {deepwS1="S~1~, "} else {deepwS1=""}
      deepS2 <- sum((biosumm[6,3] - biosumm[6,4])<0.00)
      if (deepS2 == 1)  {deepwS2="S~2~, "} else {deepwS2=""}
      deepS3 <- sum((biosumm[9,3] - biosumm[9,4])<0.00)
      if (deepS3 == 1)  {deepwS3="S~3~, "} else {deepwS3=""}      
      deepS4 <- sum((biosumm[12,3] - biosumm[12,4])<0.00)
      if (deepS4 == 1)  {deepwS4="S~4~, "} else {deepwS4=""}  
      deepS5 <- sum((biosumm[15,3] - biosumm[15,4])<0.00)
      if (deepS5 == 1)  {deepwS5="S~5~, "} else {deepwS5=""}
      deepsfem    <- paste(deepwS1,deepwS2,deepwS3,deepwS4,deepwS5,sep="")
      deepsfema   <- substr(deepsfem, 1, nchar(deepsfem)-2)   # trim trailing comma
      deepsfemale <- sub(",([^,]*)$", " and\\1", deepsfema)   # replace last comma with and
    
      # INLET SUMMARY year one -------------------------------------------------------------------------------------
      
      bio.Inlet.yr1      <-   paste(" select locality, null as depth, PropMales, PropFemales,",
                                    " MalesMnFkLen, FemalesMnFkLen, TaggedMnFkLen ", 
                                    " from  gfbio_sable_bio_summary ",
                                    " where depth is null and (TRADITIONAL_INLET_LOCALITY = 1) and year = ", yr,
                                    " order by Locality", sep="")
      #biosumm.Inlet.yr1  <-   GetSQLData(bio.Inlet.yr1,"Sablefish")
      #write.table( biosumm.Inlet.yr1, file = paste(path,'results15.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")
      biosumm.Inlet.yr1  <- read.csv(paste(path,'results15.csv',sep=''),header=T)

      colnames(biosumm.Inlet.yr1) <-  c("Spatial","Depth", "Males","Females","Males","Females","Tagged")

      biosumm.Inlet.yr1[5,3] <- round((biosumm.Inlet.yr1[1,3] + biosumm.Inlet.yr1[2,3] + biosumm.Inlet.yr1[3,3] + biosumm.Inlet.yr1[4,3])/4,2)
      biosumm.Inlet.yr1[5,4] <- round((biosumm.Inlet.yr1[1,4] + biosumm.Inlet.yr1[2,4] + biosumm.Inlet.yr1[3,4] + biosumm.Inlet.yr1[4,4])/4,2)
      biosumm.Inlet.yr1[5,5] <- round((biosumm.Inlet.yr1[1,5] + biosumm.Inlet.yr1[2,5] + biosumm.Inlet.yr1[3,5] + biosumm.Inlet.yr1[4,5])/4,0)
      biosumm.Inlet.yr1[5,6] <- round((biosumm.Inlet.yr1[1,6] + biosumm.Inlet.yr1[2,6] + biosumm.Inlet.yr1[3,6] + biosumm.Inlet.yr1[4,6])/4,0) #female mean fork
      biosumm.Inlet.yr1[5,7] <- round((biosumm.Inlet.yr1[1,7] + biosumm.Inlet.yr1[2,7] + biosumm.Inlet.yr1[3,7] + biosumm.Inlet.yr1[4,7])/4,0)
  
      inlet.deanburke.yr1 <- sum((biosumm.Inlet.yr1[1,3] - biosumm.Inlet.yr1[1,4])<0.00)
      inlet.finlay.yr1    <- sum((biosumm.Inlet.yr1[2,3] - biosumm.Inlet.yr1[2,4])<0.00)
      inlet.gil.yr1       <- sum((biosumm.Inlet.yr1[3,3] - biosumm.Inlet.yr1[3,4])<0.00)
      inlet.portland.yr1  <- sum((biosumm.Inlet.yr1[4,3] - biosumm.Inlet.yr1[4,4])<0.00)
      
      # -- determine the inlet year 1 wording for proportions
      if (inlet.deanburke.yr1 == 1 && inlet.finlay.yr1 ==1 && inlet.gil.yr1==1 && inlet.portland.yr1==1)  {inlet.words.yr1="all"}
      if (inlet.deanburke.yr1 == 1 && inlet.finlay.yr1 ==1 && inlet.gil.yr1==1 && inlet.portland.yr1==0)  
          {inlet.words.yr1="Dean/Burke Channel, Finlayson Channel and Gil Island"}
      if (inlet.deanburke.yr1 == 1 && inlet.finlay.yr1 ==1 && inlet.gil.yr1==0 && inlet.portland.yr1==0)  
          {inlet.words.yr1="Dean/Burke Channel and Finlayson Channel"}
      if (inlet.deanburke.yr1 == 1 && inlet.finlay.yr1 ==1 && inlet.gil.yr1==0 && inlet.portland.yr1==1)  
          {inlet.words.yr1="Dean/Burke Channel, Finlayson Channel and Portland Inlet"}
      if (inlet.deanburke.yr1 == 1 && inlet.finlay.yr1 ==0 && inlet.gil.yr1==0 && inlet.portland.yr1==1)  
          {inlet.words.yr1="Dean/Burke Channel and Portland Inlet"}  
      if (inlet.deanburke.yr1 == 0 && inlet.finlay.yr1 ==1 && inlet.gil.yr1==0 && inlet.portland.yr1==1)  
          {inlet.words.yr1="Finlayson Channel and Portland Inlet"} 
      if (inlet.deanburke.yr1 == 0 && inlet.finlay.yr1 ==1 && inlet.gil.yr1==1 && inlet.portland.yr1==0)  
          {inlet.words.yr1="Finlayson Channel and Gil Island"} 
      if (inlet.deanburke.yr1 == 0 && inlet.finlay.yr1 ==1 && inlet.gil.yr1==1 && inlet.portland.yr1==1)  
          {inlet.words.yr1="Finlayson Channel, Gil Island and Portland Inlet"}   
      if (inlet.deanburke.yr1 == 0 && inlet.finlay.yr1 ==0 && inlet.gil.yr1==1 && inlet.portland.yr1==1)  
          {inlet.words.yr1="Gil Island and Portland Inlet"} 
      
      femaleRange.yr1 <- range(biosumm.Inlet.yr1[,4]) * 100
      
     # -- other fish counts
     othfish      <-   paste(" select species_name, SUM(Sample_count) AS count   ",
                             " from dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH ",
                             " where (Year = ", yr, ") group by species_name, species ",
                             " ORDER BY species", sep="")
     #otherfish    <-   GetSQLData(othfish,"Sablefish")
     #write.table(otherfish , file = paste(path,'results17.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")     
     otherfish    <-    read.csv(paste(path,'results17.csv',sep=''),header=T)
     
```

## SABLEFISH SAMPLING
### `r yr` Survey

A detailed breakdown of the fate of the catch in each trap for the `r yr` survey is listed in Appendix \@ref(app:seventh-appendix). 

During the `r yr` StRS, a total of `r format(count.sample.yr1[3,2], big.mark=",")` sablefish were caught.   Of that total, `r format(count.sample.yr1[3,5], big.mark=",")` were tagged and released and `r format(count.sample.yr1[3,7], big.mark=",")` were retained for biological sampling. Of the tagged fish, `r count.sample.yr1[3,3]` were previously tagged fish that were re-released with a new tag.  Another `r count.sample.yr1[3,4]` previously tagged fish were retained for sampling (Appendix \@ref(app:nineth-appendix)).

Over the `r yr` standardized offshore sets, a total of `r format(count.sample.yr1[2,2], big.mark=",")` sablefish were caught. Of that total, `r format(count.sample.yr1[2,7], big.mark=",")` were retained for biological sampling and `r count.sample.yr1[2,3]` were previously tagged fish that were re-released with a new tag (Appendix \@ref(app:nineth-appendix)).

Out of the `r format(count.sample.yr1[1,2], big.mark=",")` sablefish captured during the `r yr` mainland inlet sets, `r format(count.sample.yr1[1,5], big.mark=",")` were tagged and released, `r format(count.sample.yr1[1,7], big.mark=",")` were used for biological sampling and `r format(count.sample.yr1[1,3], big.mark=",")` were previously tagged fish re-released with a new tag (Appendix \@ref(app:nineth-appendix)). 

Overall, the StRS sets had a higher proportion of females than males over `r stratafemale`.  More females than males were seen in the shallow depth stratum within `r shallsfemale`.  In the mid depth stratum, there were more males than females in `r midsmale`.  The deepest depth stratum saw more females in `r deepsfemale`. The mean fork length for females reached  `r as.character(round(newdata[16,6]/10,1))` cm in area S~4~ (Table \@ref(tab:Table9)).

The four northern offshore indexing localities of Langara Island-North Frederick, Hippa Island, Buck Point and Gowgaia Bay had a higher proportion of females than males. The remaining south offshore indexing localities had a higher proportion of males than females, with the exception of Esperanza Inlet. The mean fork length for females was 67.4 cm (Table \@ref(tab:Table10)).

More females than males were sampled in `r inlet.words.yr1` mainland inlet localities and samples ranged from `r femaleRange.yr1[1]` to `r femaleRange.yr1[2]` percent females. The mean fork length for females was `r as.character(round(biosumm.Inlet.yr1[5,6]/10,1))` cm (Table \@ref(tab:Table11)). 
 


```{r SamplingWords2, echo=FALSE}

     # inline text query Sablefish.dbo.GFBIO_RESEARCH_SAMPLE_DETAILS for the counts of Sablefish from all sets
     sample.yr2  <- paste("select rt.SABLE_SET_TYPE, ",
                         "SUM(sd.[Total Count])                           AS count, ",
                         "SUM(sd.[Recovered Number])                      AS tagagainlive, ",
                         "SUM(sd.[Recovered Dead Number])                 AS tagdead, ",
                         "SUM(sd.[Tagged Number] + sd.[Recovered Number]) AS tagrelease, " ,
                         "SUM(sd.[Fork Len Tag Sample Count])             AS taglengthsample,  " ,
                         "SUM(sd.Sample_count)                            AS samplecount " ,
                         "from dbo.GFBIO_RESEARCH_SAMPLE_DETAILS AS sd INNER JOIN " ,         
                         "dbo.GFBIO_SABLEBIO_TRIP_SET AS rt ON " ,
                         "sd.TRIP_ID = rt.TRIP_ID AND  sd.[SET] = rt.SET_NUMBER " ,
                         "where (sd.Year =", yr+1,") group by rt.SABLE_SET_TYPE", sep="") 
    
      #count.sample.yr2   <- GetSQLData(sample.yr2,"Sablefish")
      #write.table(count.sample.yr2 , file = paste(path,"results11.csv",sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",") 
      count.sample.yr2   <-  read.csv(paste(path,'results11.csv', sep=''), header=T) 
      
      # -- StRS year two
      bio.2      <-   paste("select locality, depth, PropMales, PropFemales, ",
                            "MalesMnFkLen, FemalesMnFkLen, TaggedMnFkLen ",
                            "from gfbio_sable_bio_summary ",
                            "where  (Depth IN (N'RD1', N'RD2', N'RD3')) and (year = ",yr + 1,
                            ") order by Locality,Depth", sep="") 
      biosumm.2  <-   GetSQLData(bio.2,"Sablefish")
      write.table(biosumm.2, file = paste(path,'results14.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",") 
      biosumm.2  <-    read.csv(paste(path,'results14.csv',sep=''),header=T) 

      colnames(biosumm.2) <-  c("Spatial","Depth","Males","Females","Males","Females","Tagged")
      biosumm.2$Spatial   <-  cleanf(biosumm.2$Spatial)  #use the remove duplicates function

      biosumm.2[16,3]     <-  round((biosumm.2[1,3] + biosumm.2[2,3] + biosumm.2[3,3])/ 3,2)
      biosumm.2[16,4]     <-  round((biosumm.2[1,4] + biosumm.2[2,4] + biosumm.2[3,4])/ 3,2)
      biosumm.2[16,5]     <-  round((biosumm.2[1,5] + biosumm.2[2,5] + biosumm.2[3,5])/ 3,0)
      biosumm.2[16,6]     <-  round((biosumm.2[1,6] + biosumm.2[2,6] + biosumm.2[3,6])/ 3,0)
      biosumm.2[16,7]     <-  round((biosumm.2[1,7] + biosumm.2[2,7] + biosumm.2[3,7])/ 3,0)
      
      biosumm.2[17,3]     <-  round((biosumm.2[4,3] + biosumm.2[5,3] + biosumm.2[6,3])/ 3,2)
      biosumm.2[17,4]     <-  round((biosumm.2[4,4] + biosumm.2[5,4] + biosumm.2[6,4])/ 3,2)
      biosumm.2[17,5]     <-  round((biosumm.2[4,5] + biosumm.2[5,5] + biosumm.2[6,5])/ 3,0)
      biosumm.2[17,6]     <-  round((biosumm.2[4,6] + biosumm.2[5,6] + biosumm.2[6,6])/ 3,0)
      biosumm.2[17,7]     <-  round((biosumm.2[4,7] + biosumm.2[5,7] + biosumm.2[6,7])/ 3,0)
      
      biosumm.2[18,3]     <-  round((biosumm.2[7,3] + biosumm.2[8,3] + biosumm.2[9,3])/ 3,2)
      biosumm.2[18,4]     <-  round((biosumm.2[7,4] + biosumm.2[8,4] + biosumm.2[9,4])/ 3,2)
      biosumm.2[18,5]     <-  round((biosumm.2[7,5] + biosumm.2[8,5] + biosumm.2[9,5])/ 3,0)
      biosumm.2[18,6]     <-  round((biosumm.2[7,6] + biosumm.2[8,6] + biosumm.2[9,6])/ 3,0)
      biosumm.2[18,7]     <-  round((biosumm.2[7,7] + biosumm.2[8,7] + biosumm.2[9,7])/ 3,0)
      
      biosumm.2[19,3]     <-  round((biosumm.2[10,3] + biosumm.2[11,3] + biosumm.2[12,3])/ 3,2)
      biosumm.2[19,4]     <-  round((biosumm.2[10,4] + biosumm.2[11,4] + biosumm.2[12,4])/ 3,2)
      biosumm.2[19,5]     <-  round((biosumm.2[10,5] + biosumm.2[11,5] + biosumm.2[12,5])/ 3,0)
      biosumm.2[19,6]     <-  round((biosumm.2[10,6] + biosumm.2[11,6] + biosumm.2[12,6])/ 3,0) 
      biosumm.2[19,7]     <-  round((biosumm.2[10,7] + biosumm.2[11,7] + biosumm.2[12,7])/ 3,0) 
      
      biosumm.2[20,3]     <-  round((biosumm.2[13,3] + biosumm.2[14,3] + biosumm.2[15,3])/ 3,2)
      biosumm.2[20,4]     <-  round((biosumm.2[13,4] + biosumm.2[14,4] + biosumm.2[15,4])/ 3,2)
      biosumm.2[20,5]     <-  round((biosumm.2[13,5] + biosumm.2[14,5] + biosumm.2[15,5])/ 3,0)
      biosumm.2[20,6]     <-  round((biosumm.2[13,6] + biosumm.2[14,6] + biosumm.2[15,6])/ 3,0)  
      biosumm.2[20,7]     <-  round((biosumm.2[13,7] + biosumm.2[14,7] + biosumm.2[15,7])/ 3,0)
      
      newdata.2           <-  rbind(biosumm.2[1:3,],   biosumm.2[16,], biosumm.2[4:6,],  biosumm.2[17,],
                                    biosumm.2[7:9,],   biosumm.2[18,], biosumm.2[10:12,],biosumm.2[19,], 
                                    biosumm.2[13:15,], biosumm.2[20,])
      newdata.2$Spatial   <-  cleanf(newdata.2$Spatial)
      
      
      colnames(newdata.2) <-  c("Spatial","Depth","Males","Females","Males","Females","Tagged")
      pdiffS1.2 <- biosumm.2[16,3] - biosumm.2[16,4] 
      pS1.2 <- sum(pdiffS1.2 < 0.00)
      
      if (pS1.2 == 1)  
         {wS1.2="S~1~, "} else {wS1.2=""}
      pdiffS2.2 <- biosumm.2[17,3] - biosumm.2[17,4]
      pS2.2<- sum(pdiffS2.2 < 0.00)
      
      if (pS2.2 == 1) 
          {wS2.2="S~2~, "} else {wS2.2=""}
      pdiffS3.2 <- biosumm.2[18,3] - biosumm.2[18,4] 
      pS3.2 <- sum(pdiffS3.2 < 0.00)
      
      if (pS3.2 == 1)  
         {wS3.2="S~3~, "} else {wS3.2=""}
      pdiffS4.2 <- biosumm.2[19,3] - biosumm.2[19,4] 
      pS4.2 <- sum(pdiffS4.2 < 0.00)
      
      if (pS4.2 == 1)  
         {wS4.2="S~4~, "} else {wS4.2=""}
      pdiffS5.2 <- biosumm.2[20,3] - biosumm.2[20,4] 
      pS5.2 <- sum(pdiffS5.2 < 0.00)
      
      if (pS5.2 == 1)  
         {wS5.2="S~5~, "} else {wS5.2=""}
      stratafem.2    <- paste(wS1.2,wS2.2,wS3.2,wS4.2,wS5.2,sep="")
      stratafema.2   <- substr(stratafem.2, 1, nchar(stratafem.2)-2)  # -- trim trailing comma
      stratafemale.2 <- sub(",([^,]*)$", " and\\1", stratafema.2)     # -- replace last comma with and
      if (stratafemale.2 == "S~1~, S~2~, S~3~, S~4~ and S~5~") {stratafemale.2="all spatial strata"}      
    
      # -- More females than males were seen in the shallow depth stratum as per yearly trend
      shallS1.2 <- sum((biosumm.2[1,3] - biosumm.2[1,4])<0.00)
      if (shallS1.2 == 1)  {shallwS1.2="S~1~, "} else {shallwS1.2=""}
      shallS2.2 <- sum((biosumm.2[4,3] - biosumm.2[4,4])<0.00)
      if (shallS2.2 == 1)  {shallwS2.2="S~2~, "} else {shallwS2.2=""}
      shallS3.2 <- sum((biosumm.2[7,3] - biosumm.2[7,4])<0.00)
      

      if (shallS3.2 == 1)  {shallwS3.2="S~3~, "} else {shallwS3.2=""}      
      shallS4.2 <- sum((biosumm.2[10,3] - biosumm.2[10,4])<0.00)

      if (shallS4.2 == 1)  {shallwS4.2="S~4~, "} else {shallwS4.2=""}  
      shallS5.2 <- sum((biosumm.2[13,3] - biosumm.2[13,4])<0.00)

      if (shallS5.2 == 1)  {shallwS5.2="S~5~, "} else {shallwS5.2=""}
      shallsfem.2    <- paste(shallwS1.2,shallwS2.2,shallwS3.2,shallwS4.2,shallwS5.2,sep="")
      shallsfema.2   <- substr(shallsfem.2, 1, nchar(shallsfem.2)-2)  # trim trailing comma
      shallsfemale.2 <- sub(",([^,]*)$", " and\\1", shallsfema.2)   # replace last comma with and
      if (shallsfemale.2 == "S~1~, S~2~, S~3~, S~4~ and S~5~") {shallsfemale.2="all spatial strata"}
      
      
      #  More males than females were seen in the mid depth stratum
      midS1.2 <- sum((biosumm.2[2,3] - biosumm.2[2,4])>0.00)
      if (midS1.2 == 1)  {midwS1.2="S~1~, "} else {midwS1.2=""}
      midS2.2 <- sum((biosumm.2[5,3] - biosumm.2[5,4])>0.00)
      if (midS2.2 == 1)  {midwS2.2="S~2~, "} else {midwS2.2=""}
      midS3.2 <- sum((biosumm.2[8,3] - biosumm.2[8,4])>0.00)
      if (midS3.2 == 1)  {midwS3.2="S~3~, "} else {midwS3.2=""}      
      midS4.2 <- sum((biosumm.2[11,3] - biosumm.2[11,4])>0.00)
      if (midS4.2 == 1)  {midwS4.2="S~4~, "} else {midwS4.2=""}  
      midS5.2 <- sum((biosumm.2[14,3] - biosumm.2[14,4])>0.00)
      if (midS5.2 == 1)  {midwS5.2="S~5~, "} else {midwS5.2=""}
      midsm.2    <- paste(midwS1.2,midwS2.2,midwS3.2,midwS4.2,midwS5.2,sep="")
      midsma.2   <- substr(midsm.2, 1, nchar(midsm.2)-2)  # trim trailing comma
      midsmale.2 <- sub(",([^,]*)$", " and\\1", midsma.2)   # replace last comma with and
      if (midsmale.2 == "S~1~, S~2~, S~3~, S~4~ and S~5~") {midsmale.2="all spatial strata"}
      
      #  More females than males were seen in the deep depth stratum
      deepS1.2 <- sum((biosumm.2[3,3] - biosumm.2[3,4])<0.00)
      if (deepS1.2 == 1)  {deepwS1.2="S~1~, "} else {deepwS1.2=""}
      deepS2.2 <- sum((biosumm.2[6,3] - biosumm.2[6,4])<0.00)
      if (deepS2.2 == 1)  {deepwS2.2="S~2~, "} else {deepwS2.2=""}
      deepS3.2 <- sum((biosumm.2[9,3] - biosumm.2[9,4])<0.00)
      if (deepS3.2 == 1)  {deepwS3.2="S~3~, "} else {deepwS3.2=""}      
      deepS4.2 <- sum((biosumm.2[12,3] - biosumm.2[12,4])<0.00)
      if (deepS4.2 == 1)  {deepwS4.2="S~4~, "} else {deepwS4.2=""}  
      deepS5.2 <- sum((biosumm.2[15,3] - biosumm.2[15,4])<0.00)
      if (deepS5.2 == 1)  {deepwS5.2="S~5~, "} else {deepwS5.2=""}
      deepsfem.2    <- paste(deepwS1.2,deepwS2.2,deepwS3.2,deepwS4.2,deepwS5.2,sep="")
      deepsfema.2   <- substr(deepsfem.2, 1, nchar(deepsfem.2)-2)   # trim trailing comma
      deepsfemale.2 <- sub(",([^,]*)$", " and\\1", deepsfema.2)   # replace last comma with and
      if (deepsfemale.2 == "S~1~, S~2~, S~3~, S~4~ and S~5~") {deepsfemale.2="all spatial strata"}
    
      
      
      # INLET SUMMARY year two-------------------------------------------------------------------------------------
      
      bio.Inlet.yr2      <-   paste(" select locality, null as depth, PropMales, PropFemales,",
                                    " MalesMnFkLen, FemalesMnFkLen, TaggedMnFkLen ", 
                                    " from  gfbio_sable_bio_summary ",
                                    " where depth is null and (TRADITIONAL_INLET_LOCALITY = 1) and year = ", yr+1,
                                    " order by Locality", sep="")
      biosumm.Inlet.yr2  <-   GetSQLData(bio.Inlet.yr2,"Sablefish")
      write.table(biosumm.Inlet.yr2, file = paste(path,'results16.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")      
      biosumm.Inlet.yr2   <-    read.csv(paste(path,'results16.csv',sep=''),header=T)

      colnames(biosumm.Inlet.yr2) <-  c("Spatial","Depth", "Males","Females","Males","Females","Tagged")

      biosumm.Inlet.yr2[5,3]  <- round((biosumm.Inlet.yr2[1,3] + biosumm.Inlet.yr2[2,3] + biosumm.Inlet.yr2[3,3] + biosumm.Inlet.yr2[4,3])/4,2)
      biosumm.Inlet.yr2[5,4]  <- round((biosumm.Inlet.yr2[1,4] + biosumm.Inlet.yr2[2,4] + biosumm.Inlet.yr2[3,4] + biosumm.Inlet.yr2[4,4])/4,2)
      biosumm.Inlet.yr2[5,5]  <- round((biosumm.Inlet.yr2[1,5] + biosumm.Inlet.yr2[2,5] + biosumm.Inlet.yr2[3,5] + biosumm.Inlet.yr2[4,5])/4,0)
      biosumm.Inlet.yr2[5,6]  <- round((biosumm.Inlet.yr2[1,6] + biosumm.Inlet.yr2[2,6] + biosumm.Inlet.yr2[3,6] + biosumm.Inlet.yr2[4,6])/4,0) #female mean fork
      biosumm.Inlet.yr2[5,7]  <- round((biosumm.Inlet.yr2[1,7] + biosumm.Inlet.yr2[2,7] + biosumm.Inlet.yr2[3,7] + biosumm.Inlet.yr2[4,7])/4,0)
  
      inlet.deanburke.yr2 <- sum((biosumm.Inlet.yr2[1,3] - biosumm.Inlet.yr2[1,4])<0.00)
      inlet.finlay.yr2    <- sum((biosumm.Inlet.yr2[2,3] - biosumm.Inlet.yr2[2,4])<0.00)
      inlet.gil.yr2       <- sum((biosumm.Inlet.yr2[3,3] - biosumm.Inlet.yr2[3,4])<0.00)
      inlet.portland.yr2  <- sum((biosumm.Inlet.yr2[4,3] - biosumm.Inlet.yr2[4,4])<0.00)
      
       # -- determine the inlet year 2 wording for proportions
      if (inlet.deanburke.yr2  == 1 && inlet.finlay.yr2  ==1 && inlet.gil.yr2 ==1 && inlet.portland.yr2 ==1)  {inlet.words.yr2 ="all"}
      if (inlet.deanburke.yr2  == 1 && inlet.finlay.yr2  ==1 && inlet.gil.yr2 ==1 && inlet.portland.yr2 ==0)  
          {inlet.words.yr2 ="Dean/Burke Channel, Finlayson Channel and Gil Island"}
      if (inlet.deanburke.yr2  == 1 && inlet.finlay.yr2  ==1 && inlet.gil.yr2 ==0 && inlet.portland.yr2 ==0)  
          {inlet.words.yr2 ="Dean/Burke Channel and Finlayson Channel"}
      if (inlet.deanburke.yr2  == 1 && inlet.finlay.yr2  ==1 && inlet.gil.yr2 ==0 && inlet.portland.yr2 ==1)  
          {inlet.words.yr2 ="Dean/Burke Channel, Finlayson Channel and Portland Inlet"}
      if (inlet.deanburke.yr2  == 1 && inlet.finlay.yr2  ==0 && inlet.gil.yr2 ==0 && inlet.portland.yr2 ==1)  
          {inlet.words.yr2 ="Dean/Burke Channel and Portland Inlet"}  
      if (inlet.deanburke.yr2  == 0 && inlet.finlay.yr2  ==1 && inlet.gil.yr2 ==0 && inlet.portland.yr2 ==1)  
          {inlet.words.yr2 ="Finlayson Channel and Portland Inlet"} 
      if (inlet.deanburke.yr2  == 0 && inlet.finlay.yr2  ==1 && inlet.gil.yr2 ==1 && inlet.portland.yr2 ==0)  
          {inlet.words.yr2 ="Finlayson Channel and Gil Island"} 
      if (inlet.deanburke.yr2  == 0 && inlet.finlay.yr2  ==1 && inlet.gil.yr2 ==1 && inlet.portland.yr2 ==1)  
          {inlet.words.yr2 ="Finlayson Channel, Gil Island and Portland Inlet"}   
      if (inlet.deanburke.yr2  == 0 && inlet.finlay.yr2  ==0 && inlet.gil.yr2 ==1 && inlet.portland.yr2 ==1)  
          {inlet.words.yr2 ="Gil Island and Portland Inlet"} 
      
      femaleRange.yr2  <- range(biosumm.Inlet.yr2[,4]) * 100  # determine range
    
      othfish2      <-   paste(" select species_name, SUM(Sample_count) AS count   ",
                             " from dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH ",
                             " where (Year = ", yr+1, ") group by species_name, species ",
                             " ORDER BY species", sep="")
     otherfish2     <-   GetSQLData(othfish2,"Sablefish")
     write.table(otherfish2 , file = paste(path,'results18.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")     
     otherfish2    <-    read.csv(paste(path,'results18.csv',sep=''),header=T) 
    
```

### 2011 Survey

A detailed breakdown of the fate of the catch in each trap for the `r yr+1` survey is listed in Appendix \@ref(app:eighth-appendix).

During the `r yr+1` StRS, a total of `r format(count.sample.yr2[3,2], big.mark=",")` sablefish were caught.   Of that total, `r format(count.sample.yr2[3,5], big.mark=",")` were tagged and released and `r format(count.sample.yr2[3,7], big.mark=",")` were retained for biological sampling. Of the tagged fish, `r format(count.sample.yr2[3,3], big.mark=",")` were previously tagged fish that were re-released with a new tag. Another `r format(count.sample.yr2[3,4], big.mark=",")` previously tagged fish were retained for sampling (Appendix \@ref(app:tenth-appendix)).

Out of the `r format(count.sample.yr2[1,2], big.mark=",")` sablefish captured during the `r yr+1` traditional survey (inlet standardized sets), `r format(count.sample.yr2[1,5], big.mark=",")` were tagged and released, and `r format(count.sample.yr2[1,7], big.mark=",")` were used for biological sampling.  Of the tagged fish, `r format(count.sample.yr2[1,3], big.mark=",")` were previously tagged fish re-released with a new tag (Appendix \@ref(app:tenth-appendix)). 

During the `r yr+1` exploratory sets, a total of `r format(count.sample.yr2[2,2], big.mark=",")` sablefish were caught.   Of that total, `r format(count.sample.yr2[2,5], big.mark=",")` were tagged and released and `r format(count.sample.yr2[2,7], big.mark=",")` were retained for biological sampling (Appendix \@ref(app:tenth-appendix)).

Overall, the StRS design sets had a higher proportion of females than males over `r stratafemale.2`.  More females than males were seen in the shallow depth stratum within `r shallsfemale.2`.  In the mid depth stratum, there were more males than females in `r midsmale.2`.  The deepest depth stratum saw more females `r deepsfemale.2`.  The mean fork length for females reached `r as.character(round(newdata.2[16,6]/10,1))` cm in area S~4~ (Table \@ref(tab:Table12)).

More females than males were sampled in `r inlet.words.yr2` traditional mainland inlet localities and samples ranged from `r femaleRange.yr2[1]` to `r femaleRange.yr2[2]` percent females.  The mean fork length for females was `r as.character(round(biosumm.Inlet.yr2[5,6]/10,1))` cm (Table \@ref(tab:Table13)).


```{r LengthDistributionsStRS}

      # StRS lengths for all years, summary from histogram figure 13
      lendata.StRS   <-  read.csv(paste(path,'figure13.csv',sep=''),header=T) 
      lendata.StRS   <-  lendata.StRS[lendata.StRS$sable_set_type == "StRS",]
      lendata.StRS   <-  lendata.StRS[lendata.StRS$year <= yr+1,]
      # unique(lendata.StRS$year)

      male.all.lendata.StRS    <-  lendata.StRS[lendata.StRS$sex ==1,]
      female.all.lendata.StRS  <-  lendata.StRS[lendata.StRS$sex ==2,]
      
      male.mean.lendata.StRS   <-  format(round(mean(male.all.lendata.StRS$length,na.rm=T),1),nsmall=1)
      female.mean.lendata.StRS <-  format(round(mean(female.all.lendata.StRS$length,na.rm=T),1),nsmall=1)
      StRS.maleCnt   <-  length(male.all.lendata.StRS$specimen_id)
      StRS.femaleCnt <-  length(female.all.lendata.StRS$specimen_id)
      
      # review
      # print(paste("males  allyear count: ",StRS.maleCnt," mean: ",male.mean.lendata.StRS,
      #          ", females   allyear count: ",StRS.femaleCnt," mean: ",female.mean.lendata.StRS,sep=""))
      
      # male and female average for StRS sites   
      # results16 from r code above re: procR_Survey_Sablefish_LenMF -- lengths and weights for all survey set types males and females
      lendata.StRS    <-    read.csv(paste(path,'results19.csv',sep=''),header=T) 
      lendata.StRS    <-    lendata.StRS[lendata.StRS$SABLE_SET_TYPE == "StRS",]

      StRS.mavgyr1    <-    lendata.StRS[lendata.StRS$Sex==1 & lendata.StRS$YEAR==yr,] 
      StRS.mavgyr2    <-    lendata.StRS[lendata.StRS$Sex==1 & lendata.StRS$YEAR==yr+1,]
      StRS.mLmean.yr1 <-    format(round(mean(StRS.mavgyr1$Length,na.rm=T),1),nsmall=1)
      StRS.mLmean.yr2 <-    format(round(mean(StRS.mavgyr2$Length,na.rm=T),1),nsmall=1)
      StRS.maleCntyr1 <-    length(StRS.mavgyr1$SPECIMEN_ID)
      StRS.maleCntyr2 <-    length(StRS.mavgyr2$SPECIMEN_ID)
    
      StRS.favgyr1    <-    lendata.StRS[lendata.StRS$Sex==2 & lendata.StRS$YEAR==yr,] 
      StRS.favgyr2    <-    lendata.StRS[lendata.StRS$Sex==2 & lendata.StRS$YEAR==yr+1,]
      StRS.fLmean.yr1 <-    format(round(mean(StRS.favgyr1$Length,na.rm=T),1),nsmall=1)
      StRS.fLmean.yr2 <-    format(round(mean(StRS.favgyr2$Length,na.rm=T),1),nsmall=1)
      StRS.femaleCntyr1 <-  length(StRS.favgyr1$SPECIMEN_ID)
      StRS.femaleCntyr2 <-  length(StRS.favgyr2$SPECIMEN_ID)
      
      # review
      #print(paste("males   year1 count: ",StRS.maleCntyr1," mean: ",StRS.mLmean.yr1,
      #            ", males   year2 count: ",StRS.maleCntyr2," mean: ",StRS.mLmean.yr2,sep=""))
      #print(paste("females year1 count: ",StRS.femaleCntyr1," mean: ",StRS.fLmean.yr1,
      #            ", females year2 count: ",StRS.femaleCntyr2," mean: ",StRS.fLmean.yr2,sep=""))
   
```
###  Length Distributions

Significant differences in length distributions between female and male sablefish are exhibited in the data collected from the StRS portion of the 2003 - `r yr+1` surveys. The mean fork length ($\bar{x}$) for the  `r format(StRS.femaleCnt, big.mark=",")` females was `r female.mean.lendata.StRS` cm and the mean fork length ($\bar{x}$) for the `r format(StRS.maleCnt, big.mark=",")` males was `r male.mean.lendata.StRS` cm (Figure \@ref(fig:figure13), a).

In `r yr`, the StRS mean fork length for the `r format(StRS.femaleCntyr1, big.mark=",")` females was `r StRS.fLmean.yr1` cm  and the average mean fork length for the `r format(StRS.maleCntyr1, big.mark=",")` males was `r StRS.mLmean.yr1 ` cm.  In `r yr+1`, the average mean fork length for the `r format(StRS.femaleCntyr2, big.mark=",")` females was `r StRS.fLmean.yr2` cm and the average mean fork length for the `r format(StRS.maleCntyr2, big.mark=",")` males was `r StRS.mLmean.yr2` cm (Figure \@ref(fig:figure13), b). 

```{r LengthDistributionsOffShore}

    # offshore lengths for all years, from histogram of male and female lengths
    lendata.Off    <-    read.csv(paste(path,'figure14.csv',sep=''),header=T) 
    lendata.Off    <-    lendata.Off[lendata.Off$SABLE_SET_TYPE == "OFFSHORE STANDARDIZED",]
    lendata.Off    <-    lendata.Off[lendata.Off$YEAR <= yr+1,]
    
    male.all.lendata.Off    <-  lendata.Off[lendata.Off$Sex ==1,]
    female.all.lendata.Off  <-  lendata.Off[lendata.Off$Sex ==2,]
    male.mean.lendata.Off   <-  format(round(mean(male.all.lendata.Off$Length,na.rm=T),1),nsmall=1)
    female.mean.lendata.Off <-  format(round(mean(female.all.lendata.Off$Length,na.rm=T),1),nsmall=1)
    Off.maleCnt   <-  length(male.all.lendata.Off$SPECIMEN_ID)
    Off.femaleCnt <-  length(female.all.lendata.Off$SPECIMEN_ID)

    # offshore lengths by past 2 years
    # procR_Survey_Sablefish_LenMF -- lengths and weights for all survey set types males and females
    lendat.Off     <-   "exec procR_Survey_Sablefish_LenMF"   
    lendata.Off   <-    GetSQLData(lendat.Off,"Sablefish")
    write.table(lendata.Off, file = paste(path,'results19.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",") 
    lendata.Off    <-    read.csv(paste(path,'results19.csv',sep=''),header=T) 
    lendata.Off    <-    lendata.Off[lendata.Off$SABLE_SET_TYPE == "OFFSHORE STANDARDIZED",]
    #  unique(lendata.Off$SABLE_SET_TYPE)
    
    # male and female average for Offshore indexing sites, 2010 was the last year of offshore site survey
    Off.mavgyr1    <-    lendata.Off[lendata.Off$Sex==1 & lendata.Off$YEAR==yr,] 
    Off.mLm.yr1    <-    format(round(mean(Off.mavgyr1$Length,na.rm=T),1),nsmall=1)
    Off.maleCntyr1 <-    length(Off.mavgyr1$SPECIMEN_ID)

    Off.favgyr1    <-    lendata.Off[lendata.Off$Sex==2 & lendata.Off$YEAR==yr,] 
    Off.fLm.yr1    <-    format(round(mean(Off.favgyr1$Length,na.rm=T),1),nsmall=1)
    Off.femaleCntyr1 <-  length(Off.favgyr1$SPECIMEN_ID)

```

Notable differences in length distributions between female and male sablefish are exhibited in the offshore indexing data of the 1990 - `r yr` surveys. The mean fork length ($\bar{x}$) for `r format(Off.femaleCnt, big.mark=",")` females was `r female.mean.lendata.Off` cm and the mean fork length ($\bar{x}$) for `r format(Off.maleCnt, big.mark=",")` males was `r male.mean.lendata.Off` cm (Figure \@ref(fig:figure14), a). 

In `r yr`, the offshore indexing mean fork length for the `r format(Off.femaleCntyr1, big.mark=",")` females was `r Off.fLm.yr1` cm and the average mean fork length for the `r format(Off.maleCntyr1, big.mark=",")` males was `r Off.mLm.yr1` cm (Figure \@ref(fig:figure14), b).


### Weight-Length 

On average for all set types, female sablefish grow faster and reach far greater size (Figure \@ref(fig:figure15), a,b) compared to males (Figure \@ref(fig:figure15), c,d).


```{r OtherFishbiosampleTextYr1, echo=FALSE,  warning=FALSE}

    other.sp   <-  read.csv(paste(path,'appendixM.csv',sep=''),header=T) # read from csv generated in appendix M

    frk.len    <-  other.sp %>% 
                   filter(morph_type == "FORK LENGTH") %>%
                   select(species_name, morph_type) %>% 
                   group_by(species_name, morph_type)
    frk.len.by.species <-  frk.len %>% tally()         # group species names and fork length type
    frk.len.sp.cnt     <-  length(frk.len.by.species$species_name)  # count the number of species
    
    tot.len    <-  other.sp %>% 
                   filter(morph_type == "TOTAL LENGTH") %>%
                   select(species_name, morph_type) %>% 
                   group_by(species_name, morph_type)
    tot.len.by.species <-  tot.len %>% tally()       # group species names and total length type
    tot.len.sp.cnt     <-  length(tot.len.by.species$species_name)
    
    snoutanal.len <-  other.sp %>% 
                   filter(morph_type == "SNOUT TO ANAL FIN LENGTH") %>%
                   select(species_name, morph_type) %>% 
                   group_by(species_name, morph_type)
    sna.len.by.species <-  snoutanal.len %>% tally()   # group species names and snout to anal fin length type
    sna.len.sp.cnt     <-  length(sna.len.by.species$species_name)
    
    total <- ""
    for (i in c(frk.len.sp.cnt:1)) {
        if (i==frk.len.sp.cnt-1){
            addition <- paste(tolower(frk.len.by.species$species_name[i]),", and ", sep="")}  # add 'and'
        else { 
            addition <- paste(tolower(frk.len.by.species$species_name[i]),", ", sep="")}  # add comma between species
        
            total    <- paste(addition,total,sep="")
     }
     total    <- gsub("pacific","Pacific", total)           # replace small p with capital
     total.frklen.string <- strtrim(total,nchar(total)-2)   # trim string

    total <- ""
    for (i in c(tot.len.sp.cnt:1)) { 
        if (i==tot.len.sp.cnt-1){
            addition <- paste(tolower(tot.len.by.species$species_name[i]),", and ", sep="")}
        else { 
            addition <- paste(tolower(tot.len.by.species$species_name[i]),", ", sep="")}
        
     total    <- paste(addition, total,sep="")
     }
     total    <- gsub("pacific","Pacific",total)
     total.totlen.string <- strtrim(total,nchar(total)-2)
     
     total <- ""
     for (i in c(sna.len.sp.cnt:1)) { 
        if (i==sna.len.sp.cnt-1){
            addition <- paste(tolower(sna.len.by.species$species_name[i]),", and ", sep="")}
        else {
            addition <- paste(tolower(sna.len.by.species$species_name[i]),", ", sep="")}
        
      total    <- paste(addition, total,sep="")
     }
     total    <- gsub("pacific","Pacific",total)
     total.snllen.string <- strtrim(total,nchar(total)-2)
     
     # print(total.frklen.string)
     # print(total.totlen.string)
     # print(total.snllen.string)

```
```{r OtherFishbiosampleTextYr2, echo=FALSE,  warning=FALSE}

    other.sp   <-  read.csv(paste(path,'appendixN.csv',sep=''),header=T) # read from csv generated in appendixN
    frk.len    <-  other.sp %>% 
                   filter(morph_type == "FORK LENGTH") %>%
                   select(species_name, morph_type) %>% 
                   group_by(species_name, morph_type)
    frk.len.by.species <-  frk.len %>% tally()
    frk.len.sp.cnt     <-  length(frk.len.by.species$species_name)
    
    tot.len    <-  other.sp %>% 
                   filter(morph_type == "TOTAL LENGTH") %>%
                   select(species_name, morph_type) %>% 
                   group_by(species_name, morph_type)
    tot.len.by.species <-  tot.len %>% tally()
    tot.len.sp.cnt     <-  length(tot.len.by.species$species_name)
    
    snoutanal.len <-  other.sp %>% 
                   filter(morph_type == "SNOUT TO ANAL FIN LENGTH") %>%
                   select(species_name, morph_type) %>% 
                   group_by(species_name, morph_type)
    sna.len.by.species <-  snoutanal.len %>% tally()
    sna.len.sp.cnt     <-  length(sna.len.by.species$species_name)
    
    total <- ""
    for (i in c(frk.len.sp.cnt:1)) {
        if (i==frk.len.sp.cnt-1){
            addition <- paste(tolower(frk.len.by.species$species_name[i]),", and ", sep="")}
      else { 
          addition <- paste(tolower(frk.len.by.species$species_name[i]),", ", sep="")}
        
     total    <- paste(addition,total,sep="")
     }
     total    <- gsub("pacific","Pacific", total)
     total.frklen.string2 <- strtrim(total,nchar(total)-2)
     # print(total.frklen.string2)

    total <- ""
    for (i in c(tot.len.sp.cnt:1)) { 
      if (i==tot.len.sp.cnt-1){
            addition <- paste(tolower(tot.len.by.species$species_name[i]),", and ", sep="")}
      else {   
            addition <- paste(tolower(tot.len.by.species$species_name[i]),", ", sep="")}
      total    <- paste(addition,total,sep="")  
      }
      total    <- gsub("pacific","Pacific", total)
      total.totlen.string2 <- strtrim(total,nchar(total)-2)
      # print(total.totlen.string2)
     
    total <- ""
    for (i in c(sna.len.sp.cnt:1)) {  
        if (i==sna.len.sp.cnt-1){
              addition <- paste(tolower(sna.len.by.species$species_name[i]),", and ", sep="")}
        else {
              addition <- paste(tolower(sna.len.by.species$species_name[i]),", ", sep="")}
        
        total    <- paste(addition, total,sep="")}
         
     total    <- gsub("pacific","Pacific", total)
     total.snllen.string2 <- strtrim(total,nchar(total)-2)
     # print( total.snllen.string2)
```


## OTHER FISH SAMPLING

Length, sex, maturity, otoliths and DNA samples were collected for the rougheye/blackspotted rockfish complex.  Length and sex were collected from all other species.  In 2010, fork length was taken for the `r total.frklen.string`; snout to anal fin length was collected for `r total.snllen.string`; total length was taken for the `r total.totlen.string` (Appendix \@ref(app:thirteenth-appendix)).  

In 2011,  fork length was taken for the `r total.frklen.string2`; snout to anal fin length was collected for `r total.snllen.string2`; total length was taken for the `r total.totlen.string2` (Appendix \@ref(app:fourteenth-appendix)).


## RECOVERED TAGGED SABLEFISH

During the `r yr` and `r yr+1` sablefish surveys, `r count.sample.yr1[1,3] + count.sample.yr1[2,3] + count.sample.yr1[3,3]` and `r count.sample.yr2[1,3] + count.sample.yr2[2,3] + count.sample.yr2[3,3]` previously tagged fish were re-released live with a new tag, respectively.  DFO has been tagging, releasing and recovering sablefish since 1991.  The highest recovery rate is within the first year of release (Table \@ref(tab:Table14)).


```{r SablefishAgesText, echo=FALSE}
   # -- provides values for inline text, important to know the last year of ages completed
   # -- sql server procedure:  procRReport_Survey_proportions_at_age which pulls age data from 
   # -- GFBIOSQL.dbo.b21_samples and b22_specimens
   age         <-  paste("select Female_Yr_Total,Age from Report_Survey_GFBIO_Age_MF_Prop where ", 
                         "SetType='StRS' and f=1 and Year=", yr +1 ,sep="")
   #agedat     <-  GetSQLData(age,"Sablefish")    # --  female age total and count of most aged text captions
   #write.table(agedat, file = paste(path,'results20.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")  
   agedat      <-   read.csv(paste(path,'results20.csv',sep=''),header=T) 
   
   oldageF     <-  paste("exec procRReport_Survey_oldAgeFish 2,",yr+1,sep="")  # -- oldest female text caption
   #oldageFem   <-  GetSQLData(oldageF,"Sablefish") 
   #write.table(oldageFem, file = paste(path,'results21.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")    
   oldageFem    <-   read.csv(paste(path,'results21.csv',sep=''),header=T) 
   
   oldageM       <-  paste("exec procRReport_Survey_oldAgeFish 1,",yr+1,sep="")  # -- oldest male text caption
   #oldageMale    <-  GetSQLData(oldageM,"sablefish") 
   #write.table(oldageMale, file = paste(path,'results22.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")    
   oldageMale    <-  read.csv(paste(path,'results22.csv',sep=''),header=T)   
   
   oldest.Female  <-  oldageFem$Age              # -- oldest female age
   oldFemYrCnt    <-  length(oldageFem$Year)     # -- count how many years that old age occurred
   oldest.Fem.Yr  <-  oldageFem$Year             # -- year captured
   oldest.Male    <-  unique(oldageMale$Age)     # -- oldest male age
   oldMaleYrCnt   <-  length(oldageMale$Year)    # -- count how many years that old age occurred
   oldest.Male.Yr <-  oldageMale$Year            # -- year captured
   
   # print(paste('female:',oldest.Female,',',oldest.Fem.Yr,sep=''))  # double check the number of years the oldest ages occur
   # print(paste('male:',oldMale,',',oldest.Male.Yr,sep=''))
```

## SABLEFISH AGES

The highest proportion of female ages in StRS sets for 2003 through to 2011 were 3, 5, 5, 6, 8, 8, 8, 10 and 12 years of age, respectively (Figure \@ref(fig:figure16), a).  The highest proportion of male ages in the StRS sets for 2003 through to 2011 were 3, 4, 5, 6, 7, 8, 9, 10 and 3 years of age, respectively (Figure \@ref(fig:figure16), b).

The highest proportion of female ages in offshore indexing sites from 1990 to 1992 were 4, 11 and 7 years of age, respectively.  A cohort appeared in 1993 through to 1998 as 3, 4, 5, 6, 7 and 8 year olds.  The years 1999 to 2003 were dominated by 5 year olds, except 2001, where 6 year olds prevailed.  Another cohort appeared in 2004 through 2010 as 4, 5, 6, 6, 8, 8 and 8 year olds, respectively  (Figure \@ref(fig:figure17), a). 

The highest proportion of male ages in offshore indexing sites from 1990 to 1992 were 4, 6 and 7 years of age, respectively.  A cohort appeared in 1993 through to 1999 as  3, 4, 6, 6, 7, 8 and 9 year olds.  The year 2000 was dominated by 5 year olds,  2001 and 2002 were dominated by 7 year olds. Another cohort appeared in 2003 through 2009 as 5, 5, 6, 6, 7, 8 and 9 year olds,  respectively.  At the time of this report, no 2010 males had been aged (Figure \@ref(fig:figure17), b).

Historic data until `r yr+1` lists the oldest female at `r oldest.Female` years of age, collected in `r oldest.Fem.Yr` and the oldest male sablefish at `r oldest.Male` years of age, collected in the year `r oldest.Male.Yr`.

```{r SablefishOceanText, echo=FALSE}
     # table SEABIRD_ReportLinePlot created in the Sablefish.dbo.Build_Seabird_tables procedure
    
     whatTrap  <-  paste("select * from SEABIRD_ACCEL_byTrap where year in(",yr,", ", yr+1,") order by [set]",sep="")
     #whatTraps <-  GetSQLData(whatTrap ,"Sablefish")  # in order to be able to comment on which traps the sensors were placed
     #write.table(whatTraps, file = paste(path,'results23.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")
     whatTraps <-   read.csv(paste(path,'results23.csv',sep=''),header=T)
     #  View(whatTraps)
     
     seabrd    <-  paste("select * from SEABIRD_ReportLinePlot where Year < ", yr+2, sep="")
     #seabird   <-  GetSQLData(seabrd ,"Sablefish") 
     #write.table(seabird, file = paste(path,'results24.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")     
     seabird   <-  read.csv(paste(path,'results24.csv',sep=''),header=T)
     #  View(seabird)
     
     yrs         <-  unique(seabird$Year)
     lavtmin     <-  min(seabird$avgtemp[seabird$depth  == "Shallow"])   # shallow water temp specs
     lavtyr      <- (seabird$Year[seabird$depth         == "Shallow" & seabird$avgtemp==lavtmin])
     lavtband1   <- (seabird$latitude[seabird$depth     == "Shallow" & seabird$Year==lavtyr & seabird$avgtemp==lavtmin]) - 0.5
     lavtband2   <- (seabird$latitude[seabird$depth     == "Shallow" & seabird$Year==lavtyr & seabird$avgtemp==lavtmin]) + 0.5
     
     lavtmax     <- max(seabird$avgtemp[seabird$depth   == "Shallow"])
     lavtyrmx    <- (seabird$Year[seabird$depth         == "Shallow" & seabird$avgtemp==lavtmax])
     lavtband1mx <- (seabird$latitude[seabird$depth     == "Shallow" & seabird$Year==lavtyrmx & seabird$avgtemp==lavtmax]) - 0.5
     lavtband2mx <- (seabird$latitude[seabird$depth     == "Shallow" & seabird$Year==lavtyrmx & seabird$avgtemp==lavtmax]) + 0.5
     
     mavt        <- min(seabird$avgtemp[seabird$depth   == "Mid"])  # mid water temp specs
     mavtyr      <- (seabird$Year[seabird$depth         == "Mid" & seabird$avgtemp  == mavt])
     mavtband1   <- (seabird$latitude[seabird$depth     == "Mid" & seabird$Year==mavtyr & seabird$avgtemp  == mavt]) - 0.5
     mavtband2   <- (seabird$latitude[seabird$depth     == "Mid" & seabird$Year==mavtyr & seabird$avgtemp  == mavt]) + 0.5
     
     mavtmx      <-  max(seabird$avgtemp[seabird$depth  == "Mid"])
     mavtyrmx    <- (seabird$Year[seabird$depth         == "Mid" & seabird$avgtemp  == mavtmx])
     mavtband1mx <- (seabird$latitude[seabird$depth     == "Mid" & seabird$Year==mavtyrmx & seabird$avgtemp  == mavtmx]) - 0.5
     mavtband2mx <- (seabird$latitude[seabird$depth     == "Mid" & seabird$Year==mavtyrmx & seabird$avgtemp  == mavtmx]) + 0.5
     
     davt        <-  min(seabird$avgtemp[seabird$depth  == "Deep"])  # deep water temp specs
     davtyr      <- (seabird$Year[seabird$depth         == "Deep" & seabird$avgtemp  == davt])
     davtband1   <- (seabird$latitude[seabird$depth     == "Deep" & seabird$Year==davtyr & seabird$avgtemp  == davt]) - 0.5
     davtband2   <- (seabird$latitude[seabird$depth     == "Deep" & seabird$Year==davtyr & seabird$avgtemp  == davt]) + 0.5  
     
     davtmx      <-  max(seabird$avgtemp[seabird$depth  == "Deep"])
     davtyrmx    <- (seabird$Year[seabird$depth         == "Deep" & seabird$avgtemp  == davtmx])
     davtband1mx <- (seabird$latitude[seabird$depth     == "Deep" & seabird$Year==davtyrmx & seabird$avgtemp  == davtmx]) - 0.5
     davtband2mx <- (seabird$latitude[seabird$depth     == "Deep" & seabird$Year==davtyrmx & seabird$avgtemp  == davtmx]) + 0.5
     
```

## OCEANOGRAPHIC TEMPERATURES AND DEPTHS
Co-plots of average temperatures and average depths by one degree latitude intervals from south-west of Vancouver Island to north-west of Haida Gwaii exhibit a general trend of decreasing temperature with depth for `r yr` and `r yr+1` (Figure \@ref(fig:figure18)).  

SBE 39 recorders have been placed on survey fishing sets since 2006. In the shallow waters (100-450 meters), the lowest to highest average temperatures were `r round(lavtmin,1)` $^\circ$C (`r lavtyr`) to  `r round(lavtmax,1)` $^\circ$C (`r lavtyrmx`).  In the mid-depth waters (450-850 meters), the lowest to highest average temperatures were `r round(mavt,1)` $^\circ$C (`r mavtyr`) to `r round(mavtmx,1)` $^\circ$C (`r mavtyrmx`).  In the deepest waters (850-1400 meters), the lowest to highest average temperatures were `r round(davt,1)` $^\circ$C (`r davtyr`) to `r round(davtmx,1)`$^\circ$C (`r davtyrmx`) (Figure \@ref(fig:figure19)).


```{r acknowledge, echo=FALSE}

    names      <-  paste(" select keyid, Association, year, Names from  dbo.ReportSurvey_Acknowlegdements where year in(", yr,",", yr+1,")", sep="")
    #credits    <-  GetSQLData(names,"Sablefish")
    #write.table(credits, file = paste(path,'results25.csv',sep=''), row.names=FALSE, na="",col.names=TRUE,  sep=",")
    credits    <-  read.csv(paste(path,'results25.csv',sep=''),header=T)
    
```    
                                                                                                        
## ACKNOWLEDGEMENTS

The stock assessment survey and data report is the result of the collaborative efforts of many individuals.  Wild Canadian Sablefish has provided coordination and support of the annual sablefish survey since 1994.  The scientific staff that conducted the sablefish research charters included `r credits[3,4]` of Archipelago Marine Research Ltd (AMR); and `r credits[4,4]` of Fisheries and Oceans, Canada. 

A special thanks to the skipper and crew of the F/V `r boat1`, whose efforts made the `r yr[1]` survey successful. In `r yr[1]`, the crew consisted of `r credits[1,4]`. Also, much appreciation  to the skipper and crew whose efforts made the `r yr+1` survey successful. In `r yr+1`, the crew consisted of `r credits[2,4]`.

\clearpage
